### 2021-01-16 SM/paper_tennantite.tex
first commit

%%
%% Copyright 2007-2019 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-num.tex 168 2019-02-25 07:15:41Z apu.v $
%%
%%
\documentclass[preprint,review,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

%%!!!!user's commands
\usepackage{amsmath}
\newcommand{\angstrom}{\text{\normalfont\AA}}

\newcommand{\hmn}[1]{% Hermann-Maguin notation
  \ensuremath{\begingroup\setupHMN #1\endgroup}%
}

\newcommand{\setupHMN}{%
  \doHMN{-}{\HMNoverline}%
  \doHMN{*}{\HMNminverse}%
  \doHMN{i}{\infty}
}

\newcommand{\doHMN}[2]{%
  \begingroup\lccode`~=`#1
  \lowercase{\endgroup\let~}#2%
  \mathcode`#1="8000
}

\newcommand{\HMNminverse}[1]{\frac{#1}{m}}
\newcommand{\HMNoverline}[1]{\mkern1mu\overline{\mkern-1mu#1\mkern-1mu}\mkern1mu}

\usepackage{miller}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{subfigure}
\usepackage[breaklinks]{hyperref}
\usepackage{graphicx}

\journal{Journal of Solid State Chemistry}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Supplementary Material \--- Laves polyhedrons in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and the lattice dynamics}

\author[TISNCM]{Alexey~A.~Yaroslavzev}
\ead{yaroslavzevalex@gmail.com}
\author[MSU,ICRAS]{Alexey~N.~Kuznetsov}
\author[SIC]{Alexander~P.~Dudka}
\author[MSU]{Andrei~V.~Mironov}
\author[MIPT,TISNCM]{Sergey~G.~Buga}
\author[TISNCM]{Vladimir~V.~Denisov}

\address[TISNCM]{Technological Institute for Superhard and Novel Carbon Materials, 108840, Troitsk, Moscow, Russia}
\address[MSU]{Department of Chemistry, Lomonosov Moscow State University, 119991, Moscow, Russia}
\address[ICRAS]{Kurnakov Institute of General and Inorganic Chemistry RAS, 119991, Moscow, Russia}
\address[SIC]{Shubnikov Institute of Crystallography of Federal Scientific Research Centre “Crystallography and Photonics” of Russian Academy of Sciences, Leninskiy Prospekt 59, 119333, Moscow, Russia}
\address[MIPT]{Moscow Institute of Physics and Technology, 141700, 9 Institutsky lane, Dolgoprudny, Russia}

\end{frontmatter}

\section{A spherical shape single-crystal X-ray diffraction study}\label{sec:level1}

A~spherical shape single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study.
Table~\ref{tab:inter_dist} and in~Table~\ref{tab:crystallographic_information} show the~comparison of previous results\cite{yaroslavzev2019} and the spherical shape single-crystal structural data.

\begin{table}
\caption{\label{tab:inter_dist}
Interatomic distances in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lccc}
Distance&
Averaged, \AA  &
Extinct, \AA  &
Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
Cu1 -- S1$\times$4   & 2.3177(17) & 2.315511)  & 2.3099(6) \\
Cu2 -- Cu21$\times$2 & 0.92(2)    & 0.891(11)  & 0.95(3) \\
Cu2 -- S1$\times$2   & 2.215(4)   & 2.211(3)   & 2.219(3) \\
Cu2 -- S2            & 2.212(7)   & 2.224(4)   & 2.206(5) \\
Cu21 -- S1$\times$2  & 2.421(18)  & 2.427(11)  & 2.427(17) \\
Cu21 -- S2           & 2.356(15)  & 2.326(11)  & 2.380(14) \\
As1 -- S1$\times$3   & 2.2505(18) & 2.2503(12) & 2.2457(19) \\
Cu21 -- As1          & 2.58(2)    & 2.604(11)  & 2.535(19) \\
Cu2 -- As1           & 3.4832(11) & 3.4816(7)  & 3.480(4) \\

\end{tabular}
}
\end{table}

\begin{table*} %The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:crystallographic_information}
Summary of crystallographic information for Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} structural experiment.}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{cccc}
&
Averaged &
Extiction&
Ref.~\cite{yaroslavzev2019}, 293~K \\

a, \AA                                                     & \multicolumn{2}{c}{10.1742(2)}	                              	             & 10.1572(2)	\\
V, \AA\textsuperscript{3}                                  & \multicolumn{2}{c}{1053.19(4)}	                              	             & 1047.91(4)	\\
S.G.                                                       & \multicolumn{3}{c}{1053.19(4)}	                                             	\\
Radiation, wavelength (\AA)                                & \multicolumn{2}{c}{Ag K\textsubscript{$\alpha$}, 0.56089}		                        	             & Mo K\textsubscript{$\alpha$}, 0.71069	\\
Diffractometer                                             & \multicolumn{2}{c}{CAD4}	                                                  & Xcalibur	\\
Absorption correction                                      & \multicolumn{2}{c}{Analytical (sphere)}	                    	             & Analytical (crystal shape)	\\
q\textsubscript{max}, deg.                                 & \multicolumn{2}{c}{29.85}	                                  	             & 42.08	\\
R\textsubscript{int}                                       & 0.041	                                                     & ---	         & 0.049	\\
N\textsubscript{ref} , collected                           & \multicolumn{2}{c}{3509}	                                    	             & 11026	\\
N\textsubscript{ref} , independent, $I\geqslant2\sigma(I)$ & 553	                                                       & 2840	         & 667	\\
N\textsubscript{paf}                                       & 50	                                                         & 55	           & 44	\\
Refinement on                                              & \multicolumn{2}{c}{$|F|^2$}	                                	             & $|F|$	\\
Anharmonic, Atoms (rank)                                   & \multicolumn{2}{c}{Cu1(4), Cu2(3), Cu21(3), S1(3), As1(3)}	  	             & Cu1(4), Cu2(3), Cu21(3), S2(4)	\\
GOF                                                        & 1.01	                                                       & 1.04	         & 1.00	\\
R/{\it w}R\textsubscript{2}                                & 0.025/0.066	                                               & 0.038/0.098	 & 0.029/0.038	\\
Min. Negative JPDF, \% of positive                         & -2.7	                                                       & 	             & -3.4	\\
$\pm\Delta\rho$, {\it e}\AA\textsuperscript{-3}            & +0.7/–0.63	                                                 & +0.95/–1.32	 & +1.7/–1.2	\\

\end{tabular}}
\end{table*}

\section{Data collection, Reduction and Model Refinement}\label{sec:level1}
A sample with the shape of an irregular parallelepiped with the sides of approximately 0.456~$\times$~0.312~$\times$~0.247~mm\textsuperscript{3} was used for the diffraction study. Five diffraction experiments were performed on Rigaku Oxford Diffraction's Xcalibur diffractometer with an EOS S2 CCD detector. Mo~K\textsubscript{$\alpha$} radiation with  $\lambda=0.71073$ \AA  wavelength was used. Measurements was made at nominal temperatures at
85, 115, 180, 250, and 293~K.
A~Cobra Plus cryosystem (Oxford Cryosystems) with an open stream of cold nitrogen directed at the specimen was used to cool.
In a process of low-temperature diffraction experiments, it was necessary to take into account a temperature gradient between the temperature sensor fixed in the nozzle of the cryostrimmer and the sample located at a distance of up to 12 mm from the sensor.
The calibration was performed\cite{Dudka2016_2}, and it shown that the actual sample temperatures were 90, 119, 182, 251, and 293~K. Data sets with a maximum reflex scattering angle of $\theta=42.0$, degrees and the data redundancy of more than 15.4 were obtained in experiments.

The calculation of integral intensities from diffraction patterns was performed using the CrysAlisPro program\cite{Rigaku}.
The data processing included: consideration of geometric features of the data collection (Lorentz correction) and correction for polarization of radiation; calibration of the diffractometer\cite{Dudka2010}; absorption correction for polyhedron samples (performed by the Gaussian integration method\cite{Busing1957}); refinement of the half-wavelength contribution\cite{Dudka2010_2}; the correction for an extinction\cite{Becker1974}.
The corrections and refinement of structural parameters were performed in the Jana2006\cite{Petek2014} and ASTRA programs\cite{Dudka2007}.
Fourier syntheses of the electron density were calculated using the Jana2006 program\cite{Petek2014}.
Graphic constructions were made in Diamond\cite{Diamont}, and Vesta programs\cite{Momma2011}.

\section{Atomic charge distribution}\label{sec:level1}

Table~\ref{tab:calc_energ} shows calculated Bader atomic charges.

\begin{table*}[t]
\caption{\label{tab:calc_energ}
Calculated Bader atomic charges in reference (0), and optimized (1-19) structures. Red marks As, and S1 charges in more covalent structures; blue marks As and S1 charges in intermediately ionic structures; bold marks the structures with an energy gain related to the reference; blue shading marks the structure with the lowest energy.
}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{ccccccccccc}
Atom                  & 0   & 1   & 2   & 3   & 4   & 5   & 6   & 7   & 8   & 9 \\
Cu1                  & +0.57	                & +0.56	                  & {\bf +0.56 }	& {\bf +0.56 }	& +0.56	& +0.56	                  & +0.56	& +0.56	& +0.56	                  & {\bf +0.56} \\
\multirow{2}{*}{Cu2} & \multirow{2}{*}{+0.49}	& \multirow{2}{*}{+0.47}	& {\bf +0.45 }	& {\bf +0.49 }	& +0.47 & +0.51	                  & +0.49	& +0.49	& +0.49	                  & {\bf +0.50} \\
		                 &		                    &                         & {\bf +0.40 }	& {\bf +0.39 }	& +0.40	& +0.47	                  & +0.39	& +0.39	& +0.45	                  & {\bf +0.46} \\
\multirow{2}{*}{S1}  & -1.41	                & -1.45	                  & {\bf -1.42 }  & {\bf -1.42 }	& -1.39	& \textcolor{red}{-0.76}	& -1.43	& -1.43	& \textcolor{blue}{-0.73}	& \textcolor{blue}{-0.70} \\
                     & -1.47	                & -1.53	                  & {\bf -1.49 }  & {\bf -1.50 }	& -1.47	& \textcolor{red}{-0.92}	& -1.53	& -1.52	& \textcolor{blue}{-1.42}	& \textcolor{blue}{-1.44} \\
S2                   & -0.88	                & -0.85	                  & {\bf -0.78 }  & {\bf -0.82 }	& -0.84	& -0.84	                  & -0.83	& -0.83	& -0.86	                  & {\bf -0.86} \\
\multirow{2}{*}{As}  & \multirow{2}{*}{+2.97}	& +3.05	                  & {\bf +3.12 }	& {\bf +3.15 }	& +3.06	& +0.86	                  & +3.11	& +3.12	& \textcolor{blue}{+2.03}	& \textcolor{blue}{+1.51} \\
	                   &                        & +2.99	                  & {\bf +2.99 }  & {\bf +3.07 }	& +3.11	& +0.93	                  & +3.06	& +3.07	& \textcolor{blue}{+1.53}	& \textcolor{blue}{+0.89} \\

Atom                  & 10   & 11   & 12   & 13   & 14   & 15   & 16   & 17   & 18   & 19 \\
Cu1                  & +0.56   & 	{\bf +0.56 }           & 	+0.56  & 	+0.56                  & 	{\bf +0.56 }           & 	+0.56                  & 	+0.56                  & 	{\bf +0.56 }           & 	{\bf +0.56 }           & 	{\bf +0.56 } \\
\multirow{2}{*}{Cu2} & +0.48   & 	{\bf +0.51 }           & 	+0.46  & 	+0.51                  & 	{\bf +0.50 }           & 	+0.51                  & 	+0.51                  & 	{\bf +0.51 }           & 	{\bf +0.51 }           & 	{\bf +0.50 } \\
		                 & +0.39   & 	{\bf +0.48 }           & 	+0.45  & 	+0.47                  & 	{\bf +0.46 }           & 	+0.46                  & 	+0.45                  & {\bf +0.46 }            & 	{\bf +0.46 }           & 	{\bf +0.46 } \\
\multirow{2}{*}{S1}  & -1.43   & 	\textcolor{red}{-0.73} & 	-1.42  & 	\textcolor{red}{-0.72} & 	\textcolor{red}{-0.73} & 	\textcolor{red}{-0.73} & 	\textcolor{red}{-0.72} & 	\textcolor{red}{-0.72} & 	\textcolor{red}{-0.74} & 	\textcolor{red}{-0.72} \\
                     & -1.52   & 	\textcolor{red}{-0.76} & 	-1.52  & 	\textcolor{red}{-0.77} & 	\textcolor{red}{-0.76} & 	\textcolor{red}{-0.77} & 	\textcolor{red}{-0.77} & 	\textcolor{red}{-0.77} & 	\textcolor{red}{-0.76} & 	\textcolor{red}{-0.76} \\
S2                   & -0.82   & 	{\bf -0.98}            & 	-0.81  & 	-0.93                  & 	{\bf -0.90 }           & 	-0.94                  & 	-0.90                  & 	{\bf -0.88 }           & 	{\bf -0.91 }           & 	{\bf -0.89 } \\
\multirow{2}{*}{As}  & +3.11   & 	\textcolor{red}{+0.94} & 	+3.07  & \textcolor{red}{+0.94}  & 	\textcolor{red}{+0.94} & 	\textcolor{red}{+0.94} & 	\textcolor{red}{+0.95} & 	\textcolor{red}{+0.95} & 	\textcolor{red}{+0.91} & 	\textcolor{red}{+0.91} \\
	                   & +3.00	 & \textcolor{red}{+0.76}	 & +2.99	 & \textcolor{red}{+0.85}	 & \textcolor{red}{+0.80}	 & \textcolor{red}{+0.84}	 & \textcolor{red}{+0.87}	 & \textcolor{red}{+0.85}	 & \textcolor{red}{+0.85}	 & \textcolor{red}{+0.84} \\
\end{tabular}}
\end{table*}

\section{Analysis of temperature dynamics of atomic displacement parameters obtained from diffraction data}\label{sec:level1}
Structural analysis allows us to determine the positions of the scattering centers of atoms, as well as the deviations of atoms from their equilibrium positions.
Atomic displacements are defined as the probability density of finding atoms in the selected point in space. In the traditional method, the corresponding contribution to the structural factor does not depend on temperature\cite{willis1975thermal}.
An alternative model for the decomposition of the atomic "thermal factor" in a series on temperature degrees has a clear physical meaning\cite{willis1975thermal}, but unfortunately, it has not widespread, as it gives the worst fit.
A very promising Bergi's approach\cite{Brgi2000} uses a dynamic matrix, but, in the proposed version, it is limited to the class of molecular crystals.
The method of complementary spectroscopic research is also relevant, when the characteristics of the phonon spectrum are taken as an initial approximation in the study of atomic motion\cite{Hoser2016}.
The reason for the inefficiency of the models, which are known to have more ”physical meaning” than the probabilistic model, is as follow.
The physics of X-rays, neutrons and electrons scattering is such that the calculated atomic displacement parameters (ADPs) may correspond to thermal vibrations supplemented with static shifts\cite{Trueblood1996}.
Hence, an account of only dynamic components is not correct. For the same reason, methods for estimating ADPs temperature dynamics based on Einstein's classical approaches are not widely used in structural and Debye analysis\cite{Einstein1907,Debye1914}.
In short, these methods are not very popular, since they don't describe experimental data and the probabilistic model.
There was an inconsistance: the multi-temperature diffraction research added much information to describe the thermodynamics of solids,
however, it was almost impossible to use this advantage since the obtained ADPs had no analytical temperature dependence.
Recently in Ref.~\cite{Dudka2019} the extended models of Einstein and Debye were proposed, which improved model and experimental data agreement to a precision of 0.3-2~\%.
The separation of the static and dynamic components in atomic displacements in crystals was carried out in two stages.

1. We did a multi temperature diffraction experiments and refinement of the structure models in a regular manner separately for each experiment. The ADP values obtained as a result of the refinement give an average estimation:
u\textsubscript{obs}(T)=u\textsubscript{eq}(T)=$\langle u^2 \rangle$=(u\textsubscript{11}+u\textsubscript{22}+u\textsubscript{33})/3

2. Further,  u\textsubscript{obs}(T) are used in a general modeling procedure to evaluate the characteristic temperatures, and analyze static and dynamic contributions to composite atomic displacements. The unknown thermodynamic parameters are refined by the LS-algorithm while minimizing the norm
$\sum [u_{calc}(T) - u_{obs}(T)]^2 \rightarrow min$.
We assume that $u_{calc}=xu_{E}+(1-x)u_{D}+u_{static}$, where $xu_{E}$ and $(1-x)u_{D}$ are Einstein and Debye parts, ustatic is a static shift of an atom from its site in the structure model.
The thermal expansion of the crystal and the corresponding change of the atomic vibration frequencies depended on temperatures and can be described using a quasi-harmonic approximation. The quasi-harmonic approximation uses Gruneisen parameter $\gamma$. U is a function of the temperature-dependent unit-cell volume:
$U = U_{harmonic}[1 + 2\gamma((V(T)-V(T_0))/V(T_{0}))]$.
Einstein or Debye temperatures are the functions of the temperature-dependent unit-cell volume $V(T)$ also:
$T_{E} = T_{E}(T_{0})[1 + \gamma((V(T)-V(T_0))/V(T_{0}))]$
$T_{0}$ is a minimal experimental temperature, for example.
The average oscillation frequency of the selected atom and its characteristic Einstein temperature, $T_{E}$, can be obtained by assuming x~$=$~1. In other words, to model the displacement of atoms that are weakly bound to their neighbors, it is better to use the extended expression for the displacement of independent harmonic oscillators (the Einstein model):
\[
u_{E}=\frac{h^2}{4\pi^2\cdot k_{b} \cdot m_{a} \cdot T_{E}} \Big(\frac{1}{2} + \frac{1}{e^{\frac{T_{E}}{T}}-1} \Big).
\]

The maximum oscillation frequency of the selected atom and its characteristic Debye temperature, $T_{D}$, corresponds to the case x~$=$~0. Therefore, the Debye model is better suited for the description of correlated displacements of atoms:
\[
u_{D}=\frac{3h^2}{4\pi^2\cdot k_{b} \cdot m_{a} \cdot T_{E}} \bigg(\frac{1}{4} + \Big(\frac{T_{E}}{T}\Big)^2 \int_{0}^{\frac{T_{E}}{T}} \frac{y}{e^{y} - 1}dy \bigg).
\]
Here: $h$ --- the Planck constant; $k_{B}$ --- the Boltzmann constant; $m_{a}$ --- atomic mass; $T_{E}(T_{D})$ --- the characteristic Einstein (Debye) temperature; T --- the temperature of the experiment. Distributions of zero--point oscillations, $u_{0E}$ or $u_{0D}$, are obtained by substituting T~$=$~0 in the Einstein or Debye formulas. Thus, the contribution of Einstein or Debye to atomic displacements consists of zero quantum vibrations, $u_{0E}$ or $u_{0D}$, and a temperature-dependent part, $u_{E}$(T) or $u_{D}$(T), which can be associated with the thermal motion of atoms. Thus, $u_{E}$ is $u_{E}=u_{0E}+u_{E}(T)$, and $u_{D}$ is $u_{D}=u_{0D}+u_{D}(T)$.
A shift of atoms from their equilibrium positions due to any reason other than thermal vibrations is the sum of zero vibrations and a static shift:
$u_{shift}=u_{0E}+u_{static}$ or $u_{shift}=u_{0D}+u_{static}$.
Thus, the new technique allows to determine the characteristic temperatures using only the structure refinement results, and to separate dynamic and static components of $u_{eq}$.
The refinable parameters of this procedure are: $T_{E}(T_{D})$ --- the characteristic Einstein (Debye) temperatures, static component $u_{static}$, and Grunaisen parameter $\gamma$. The contribution of quantum zero vibrations is calculated separately.

\section{Electron microscopy}\label{sec:level1}
High-resolution electron microscopy images were obtained using FEI~Titan~80--300 transmission electron microscope in the HAADF--STEM mode (scanning translucent) with the acceleration voltage of 300~kV.
The sample for microscopy was prepared using FEI~Helios~600 focused ion beam setup.
The HAADF image with the tennantite crystal [110]  zone generated by VESTA\cite{Momma2011} is shown in Fig.~\ref{fig:haadf_overlay}.

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{mic_cu12as4s13_110}% Here is how to import EPS art
\caption{\label{fig:haadf_overlay} Left --- the tennantite crystal [110] zone  generated  by VESTA\cite{Momma2011}; rigth --- the HAADF image with the tennantite crystal [110] zone.}
\end{figure}

The full HAADF image with the tennantite crystal [110] zone and  transmission electron diffraction are shown in Fig.~\ref{fig:TEM}.

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.2\textwidth]{mic_Figure_10}}
 \quad
\subfigure{\includegraphics[width=0.2\textwidth]{difr01_el_mic_zone_110}}
\caption{\label{fig:TEM} Left --- the HAADF image with the tennantite crystal [110] zone , right --- transmission electron diffraction of the same zone. }
\end{figure}

\section{References}\label{sec:level1}
\bibliographystyle{elsarticle-num}
\bibliography{reff}

\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2021-01-16 paper_tennantite.tex
first commit

%%
%% Copyright 2007-2019 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-num.tex 168 2019-02-25 07:15:41Z apu.v $
%%
%%
\documentclass[preprint,review,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

%%!!!!user's commands
\usepackage{amsmath}
\newcommand{\angstrom}{\text{\normalfont\AA}}

\newcommand{\hmn}[1]{% Hermann-Maguin notation
  \ensuremath{\begingroup\setupHMN #1\endgroup}%
}

\newcommand{\setupHMN}{%
  \doHMN{-}{\HMNoverline}%
  \doHMN{*}{\HMNminverse}%
  \doHMN{i}{\infty}
}

\newcommand{\doHMN}[2]{%
  \begingroup\lccode`~=`#1
  \lowercase{\endgroup\let~}#2%
  \mathcode`#1="8000
}

\newcommand{\HMNminverse}[1]{\frac{#1}{m}}
\newcommand{\HMNoverline}[1]{\mkern1mu\overline{\mkern-1mu#1\mkern-1mu}\mkern1mu}

\usepackage{miller}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{subfigure}
\usepackage[breaklinks]{hyperref}
\usepackage{graphicx}

\journal{Journal of Solid State Chemistry}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Laves polyhedrons in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and the lattice dynamics}

\author[TISNCM]{Alexey~A.~Yaroslavzev}
\ead{yaroslavzevalex@gmail.com}
\author[MSU,ICRAS]{Alexey~N.~Kuznetsov}
\author[SIC]{Alexander~P.~Dudka}
\author[MSU]{Andrei~V.~Mironov}
\author[MIPT,TISNCM]{Sergey~G.~Buga}
\author[TISNCM]{Vladimir~V.~Denisov}

\address[TISNCM]{Technological Institute for Superhard and Novel Carbon Materials, 108840, Troitsk, Moscow, Russia}
\address[MSU]{Department of Chemistry, Lomonosov Moscow State University, 119991, Moscow, Russia}
\address[ICRAS]{Kurnakov Institute of General and Inorganic Chemistry RAS, 119991, Moscow, Russia}
\address[SIC]{Shubnikov Institute of Crystallography of Federal Scientific Research Centre “Crystallography and Photonics” of Russian Academy of Sciences, Leninskiy Prospekt 59, 119333, Moscow, Russia}
\address[MIPT]{Moscow Institute of Physics and Technology, 141700, 9 Institutsky lane, Dolgoprudny, Russia}

\begin{abstract}
Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedride group of minerals with a low lattice thermal conductivity.
The atomic displacement parameters and low-energy optical phonon modes are discussed within the context of the structure variations and percularities of the charge distributions.
The latter indicates that the tennantite structure tends to conform to the covalent, asymmetric bonds and inconsistent electronic densities.
Accoding to the DFT calculations results, varying shifts of copper atoms in Laves polyhedron are featured in the unit cells with very close total energies with deviation less than 0.24~eV, which can explain the observed behavior of the atomic displacement parameters.
A specially designed  technique used for the experimental analysis of the atomic displacement parameters  revealed Einstein characteristic temperatures in the tennantite structure to be in the range of 50--190~K, attributed to  low-energy optical phonon modes.

\section*{Highlights}
\begin{itemize}
  \item Synthetic tennantite Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} structure consists of disordered Laves polygons
  \item DFT calculations reveal a mixed valence of Cu atoms, and Laves polygon distortions
  \item Jahn-Teller distortions give rise to a set of unit cells with close ground energies
  \item Rattling vibration modes refer to Einstein’s temperatures of 74, 104, 115, 185K
\end{itemize}

\end{abstract}

\begin{keyword}
tennantite Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}\sep
thermoelectic materials\sep
anisotropy\sep
optical spectroscopy\sep
X-ray diffraction\sep
computer simulations\sep

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
% \section{}
% \label{}
\section{Introduction}\label{sec:level1}

The tennantite-tetrahedride group of minerals represents a large class of inorganic compounds including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.

Despite being known for over two centuries, these minerals are still under investigation, both due to  structural peculiarities and potential applications. Arsenic- and antimony-containing compounds of this class are the advanced thermoelectric materials with a low lattice thermal conductivity\cite{Sootsman2009,Chetty2015}. Understanding the relationships between the crystal structure and phonon propagation, and scattering, is of a prime importance for designing new thermoelectric materials.

In a case of tennantite- and tetrahedrite-based materials, it is generally considered, that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen p orbitals\cite{Lai2015}.
Such a hybridization leads to a bonding asymmetry, and out-of-plane low frequency rattling modes, which are quasi-localized and anharmonic\cite{May2016,Bouyrie2015}.

Some authors note\cite{DiBenedetto2005,Tanaka2015}, that asymmetric bonds give rise to magnetic properties and, in some cases, to antiferromagnetic ordering\cite{yaroslavzev2019,Blandy_2018}.
In both kinds of materials, deviations from the Curie-Weiss law in the temperature dependencies of the magnetization were revealed: at 124~K\cite{Hathwar2019} in tennantite, and at 84~K\cite{Nasonova2016_2} in tetrahedrite.

According to the structural study, these deviations take place due to the distortion of S\textsubscript{2}Cu\textsubscript{6} octahedra\cite{Tanaka2015}.
The distortion at 84 K in tetrahedrite is reported to lead to either the symmetry lowering from \hmn{I -4 3 m} to \hmn{I -4 2 m}  space group accompanied by the displacement of S atoms\cite{Hathwar2019}, or to a shift of Cu2 atoms towards S\textsubscript{3} triangle plane with S\textsubscript{2} displacement\cite{Nasonova2016_2} in the same symmetry, and space group.

Recently, we performed a multi-temperature (90--298~K) structural study of a synthetic tennantite\cite{yaroslavzev2019} and found that below ca. 120 K the copper atom distribution in tennantite changes from a more statistically delocalized Cu2 a well-defined split into Cu2 and Cu21 positions without a first-order phase transition.
This effect is accompanied by As1 and S2 atoms displacement, which was also observed in ref.~ \cite{Hathwar2019}.
We also investigated the low- and room-temperature electronic structures of a synthetic tennantite based on the DFT calculations, which confirmed the second-order transition from the low-temperature AFM state to the room-temperature PM state\cite{yaroslavzev2019}.

However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves polyhedra in the structure, were left aside in the previous paper\cite{yaroslavzev2019}.
In this paper, we focus on these problems, and  investigate the tennantite cell energy distribution, and the charge density differences for different Cu positions in Cu$_{6}^{II}$S$^{II}$.
Also, we consider low-energy phonon modes, and peculiarities of the atomic displacement parameters in the temperature range of 85--293~K, the same as in Ref.~\cite{Dudka2019}, in a context of the cell energy distribution.
To clarify distortions in Cu$_{6}^{II}$S$^{II}$ octahedra, a study of the spherical single-crystal sample was performed and  the high-angle annular dark-field (HAADF) image was obtained.

\section{Materials and methods}\label{sec:level1}
\subsection{Synthesis}\label{sec:level2}

High quality single crystals of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} for the XRD analysis were grown using a two-step procedure. At first, bulk Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} has been prepared by a high-temperature technique from copper (99.5~\%), arsenic (99.5~\%), and sulfur (99.5~\%).
Then, the ingots were subjected to directional recrystallization by the Bridgman-Stockbarger technique in a two-zone furnace.
The temperature in the recrystallization zone was chosen 40 K~above the tennantite melting point. A speed of the  ingot motion was 0.5~mm/hour, with the temperature gradient in the recrystallization zone about 8--10~K/mm.

\subsection{Single-crystal X-ray diffraction}\label{sec:level2}
A spherical shape single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study.
Enraf-Nonius CAD-4 diffractometer with AgK\textsubscript{$\alpha$} and graphite monochromator was used.
The spherical shape single-crystal structural study results are presented in Appendix, they are compared with the structural data of the irregular form sample\cite{yaroslavzev2019}.

\subsection{Analysis of temperature dynamics of atomic displacements}\label{sec:level2}
The temperature dynamics of an atomic displacement from the previous study\cite{yaroslavzev2019} were used to estimate Einstein characteristic temperatures by the mixed Einstein-Debye model using DebyeFit program\cite{Dudka2019}.
The data are based on the study of  Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} single-crystal sample at 85, 115, 180, 250, and 293~K.
The sample has a rectangular shape with the dimensions of 0.456~$\times$~0.31~$\times$~0.247~mm\textsuperscript{3}.
Xcalibur diffractometer equipped with a CCD EOS S2 detector (Rigaku Oxford Diffraction), MoK\textsubscript{$\alpha$} and Cobra Plus (Oxford Cryosystems) with nitrogen gas flow were used.
The original experimental methods and data processing are presented in Appendix in details.

\subsection{Theoretical calculations}\label{sec:level2}
Calculations of the stability of possible tennantite polytypes were performed based on Density Function Theory (DFT)\cite{Kohn1965} within the generalized gradient approximation (GGA) using Perdew-Burke-Ernzerhof exchange-correlation functional\cite{Perdew1996}.
We used the projector augmented wave method\cite{Blchl1994} with the periodic boundary conditions as implemented in Vienna Ab-initio Simulation Package (VASP)\cite{Kresse1996,Kresse1996-2,Kresse1993,Kresse1994}.
The plane-wave energy cut-off was set to 450~eV. To calculate the equilibrium atomic structure, the Brillouin zone was sampled according to the Monkhorst–Pack scheme\cite{Monkhorst1976} with a 6$\times$6$\times$6 grid in the k-space. The convergence criterion for the structural relaxation was set at 0.1~meV.
Both the unit cell symmetry and parameters were allowed to relax.
To facilitate unconstrained structural optimization, all the starting structures were converted to \hmn{P1} space group.

\subsection{Electron microscopy}\label{sec:level2}
High-resolution electron microscopy images were taken using FEI~Titan~80--300 transmission electron microscope in the HAADF--STEM mode (scanning translucent) with an acceleration voltage of 300~kV. The sample for microscopy was prepared using FEI~Helios~600 focused ion beam setup. HAADF image was fitted by Atomap\cite{Nord2017} package in Python.

\subsection{Raman Spectroscopy}\label{sec:level2}
Raman spectroscopy study was performed with a spectrometer TRIAX-552, equipped with Peltier TE-cooled detector CCD~SPEC~10~(Princeton Instruments).
A grating of 600~lines~mm\textsuperscript{-1}, and a 50\textsuperscript{$\times$} lens Mitutoyo~M~Plan~Apo~SL50 (a numerical aperture of 0.42) were used. Raman spectra was excited with 514.5~nm argon-ion laser Spectra-Physics Stabilite 2017 with 1~mW output power on a sample. An open argon gas flow was used to reduce air’s modes.
Calibration was performed using 520.5~cm\textsuperscript{-1} Raman peak of a polished silicon wafer. For observation of lines near the laser line we used 3~ONDAX~114-ER297-001 fiber Bragg gratings. Fittings of the Raman spectra were performed by the LMFIT\cite{LMFIT} package in Python. The fitting model was based on 6 pseudo-Voigt functions and a polynomial function for the background.

\section{Result and discussion}\label{sec:level1}

\subsection{Remarks on the structure of synthetic tennantite}\label{sec:level2}
Study of the high-grade single crystal allowed us to re-investigate the crystal structure of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  with a high precision.
Our data confirms that the compound contains 12 copper atoms per formula unit, and shows no evidences of a copper deficiency.
Neither XRD, nor TEM data shown defects.
Due to the crystal growth method used, we suspected a possibility of anisotropic extinction.
The intensity vs  $\psi$ angle were measured for several reflections to analyze this effect.

The results are presented in Fig.~\ref{fig:rock_curv} .
All curves were approximated by the least-square fitting.
Only for \hkl[4 0 0], \hkl[0 4 0], and \hkl[0 0 4] reflections the coefficients with $x$ and $x^{2}$ were in the range of 5--8$\sigma$, while for the two other sets they were about $\sigma$ or less (with one 2$\sigma$ exception).
Thus, we conclude that the intensities of weak reflections at small angles and reflections at high angles have fixed $\psi$ angles.
On the contrary, $\psi$ angles of strong reflections with small $\sin\theta/\lambda$ vary, that may indicate an anisotropic extinction.

\begin{figure*}
\centering
\subfigure{\includegraphics[width=0.3\textwidth]{200}}
 \quad
\subfigure{\includegraphics[width=0.3\textwidth]{400}}
 \quad
\subfigure{\includegraphics[width=0.3\textwidth]{1200}}
\caption{\label{fig:rock_curv} Normalized intensities of reflections vs. $\psi$ angle; left --- 200, 020, 002 (weak, sin=0.098), middle --- 400, 040, 004 (strong, sin=0.197), right --- 1200, 0120, 0012 (moderate, sin=0.590).}
\end{figure*}

\begin{table}
\caption{\label{tab:anis_ext}%
Anisotropic extinction parameters in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{cccccc}

\textrm{ g\textsubscript{11}$\times$10\textsuperscript{4}}&
\textrm{ g\textsubscript{22}$\times$10\textsuperscript{4}}&
\textrm{ g\textsubscript{33}$\times$10\textsuperscript{4}}&
\textrm{ g\textsubscript{12}$\times$10\textsuperscript{4}}&
\textrm{ g\textsubscript{13}$\times$10\textsuperscript{4}}&
\textrm{ g\textsubscript{23}$\times$10\textsuperscript{4}}  \\
1.4(4)	& 4.2(8)	& 2.7(4)	& 1.0(3) &	0.2(3)	& -1.1(5) \\
\end{tabular}}
\end{table}

The extinction can be explained by the dynamic disorder of Cu21 atoms. Such a disorder is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
The electron diffraction, and overlay of HAADF image with the tennantite crystal [110] zone generated by VESTA\cite{Momma2011}, are shown in Appendix.
The processed HAADF image (Fig.~\ref{fig:micro} right) shows  the ellipticity for the Cu/As atomic columns, which is a measure of the atomic column elongation\cite{Nord2017}.
The atomic column elongation is explained by the blurring of the intensity distribution, and a large atomic displacement.
A similar inhomogeneous electron density was observed in tetrahedrite\cite{Mishra2017}, and tetrahedral framework structure\cite{Suekuni2019}.
Also, the anisotropy may be caused by the crystal growth conditions or/and a crystal cell distortion.
If so, then the structure would have a diagonal distortion or/and have more or less than 12 copper atoms per cell, which is not the case.

\begin{figure}[ht]
\centering
\subfigure{\includegraphics[width=0.35\columnwidth]{mic_Figure_10}}
 \quad
\subfigure{\includegraphics[width=0.49\columnwidth]{CuAs_raws_normal}}
\caption{\label{fig:micro} Left --- the HAADF image of tennantite crystal viewed from the [110] zone; right --- the processed HAADF image with the ellipticity for the Cu/As atomic columns. The analysis implied quantifying the positions and shapes of atomic columns based on Atomap\cite{Nord2017}. }
\end{figure}

\subsection{Atomic displacement parameters analysis of the temperature dynamics based on diffraction data}\label{sec:level2}

The atomic displacement parameters (ADPs) were analyzed by DebyeFit program using the structural data.
The DebyeFit estimates the Debye or/and Einstein characteristic temperature in crystals from the equivalent atomic displacement parameters obtained at different temperatures.

At fitting, ADPs are considered as a combination of quantum zero vibrations, thermal vibrations, and static shifts\cite{Trueblood1996,Bentien2005,Nakatsuka2011}.
The thermal expansion of the crystal, and the corresponding change of the atomic vibration frequencies depend on the temperature, and may be described using a quasi-harmonic approximation\cite{willis1975thermal,Bentien2005}.
As a result ADP, is described by u\textsubscript{calc}=xu\textsubscript{E}+(1-x)u\textsubscript{D}+u\textsubscript{static}, where xu\textsubscript{E} and (1-x)u\textsubscript{D} are Einstein and Debye parts, u\textsubscript{static} is a static shift of an atom from its site in the structure model\cite{Dudka2019}.
The result of tennantite ADPs fitting is presented in the Fig.~\ref{fig:enst_temp}, and Table~\ref{tab:enst_temp}.
The average oscillation frequency of the selected atom, and its characteristic Einstein temperature, T\textsubscript{E}, can be obtained  assuming x~$=$~1.
The maximal oscillation frequency of the selected atom and its characteristic Debye temperature, T\textsubscript{D}, corresponds to the case x~$=$~0.
Distributions of zero-point oscillations, u\textsubscript{$0E$} or u\textsubscript{$0D$}, were obtained applying T~$=$~0 in the Einstein or Debye formulas.
Thus, the contribution of Einstein or Debye parts to atomic displacements consists of zero quantum vibrations, u\textsubscript{$0E$} or u\textsubscript{$0D$}, and a temperature-dependent part, u\textsubscript{E}(T) or u\textsubscript{D}(T), which can be associated with the thermal motion of atoms.
That is, u\textsubscript{E} = u\textsubscript{$0E$} + u\textsubscript{E}(T), and u\textsubscript{D} = u\textsubscript{$0D$} + u\textsubscript{D}(T). The shift of an atom from its equilibrium position due to any reason other than thermal vibrations is the sum of zero vibrations and static shift: u\textsubscript{shift} = u\textsubscript{$0E$} + u\textsubscript{static} or u\textsubscript{shift} = u\textsubscript{$0D$} + u\textsubscript{static}\cite{Dudka2019}.

A good agreement between model ADP, u\textsubscript{calc}, and equivalent experimental ADP, u\textsubscript{eq}, can be obtained only if (1) the temperature of the crystal is correctly determined during the measurements; (2) the static shift of the atoms is taken into account, i.e. when using the extended model with  inclusion u\textsubscript{static} term. The fitting results are presented in Figure~\ref{fig:enst_temp}.

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{ADP_aproximation_eng}% Here is how to import EPS art
\caption{\label{fig:enst_temp} Equivalent parameters U\textsubscript{eq} of the mean-square displacements of atoms in tennantite. Points are the experimental data. The solid curves show the fit of the temperature dependences according to the expanded Einstein model.}
\end{figure}

Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) indicate the potential instability of this position. Even after dividing Cu2 position into Cu2 and Cu21, the Cu2 position remains highly disordered. This disordering is reliably described by the anharmonic model of atomic displacements using the Gram-Charlier expansion to the 4th order.

\begin{table}
\caption{\label{tab:enst_temp}
Einstein temperatures, dispersions of zero-point oscillations u\textsubscript{$E_{0}$} u\textsubscript{static}, and u\textsubscript{shift} for atoms in tennantite. $R=\sum |u\textsubscript{eq} - u\textsubscript{calc} |/\sum u\textsubscript{eq}$ is the residual factor of the LS procedure.
}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{cccccc}

&
\textrm{ T(Einstein)~K, cm\textsuperscript{-1}}&
\textrm{ u\textsubscript{E}$\times$10\textsuperscript{4}, $\angstrom^{2}$  }&
\textrm{ u\textsubscript{static}$\times$10\textsuperscript{4}, $\angstrom^{2}$     }&
\textrm{ u\textsubscript{shift}$\times$10\textsuperscript{4}, $\angstrom^{2}$    }&
\textrm{ R,  \% }  \\

Cu\textsubscript{1}	  & 115.0(1.9), 79.9     & 3.3	& 0.9(0.4) & 4.2 & 	1.89 \\
Cu\textsubscript{2}	  & 103.9(5.5), 72.2  & 3.7	& 12.0(1.5) & 15.7 & 	3.28 \\
Cu\textsubscript{21}  & 74.0(5.2), 51.4	   & 5.2	& 1.7(4.0) & 6.8 & 8.06 \\
As\textsubscript{1}	  & 185.2(8.1), 128.7 & 1.7	& 5.4(0.3) & 7.2 & 	2.20 \\

\end{tabular}}
\end{table}

\subsection{Analysis of anharmonic vibrations of copper atoms through the ADP and Raman spectroscopy}\label{sec:level2}

The Raman spectrum of the crystalline tennantite consists of the following well-defined peaks: $\nu_{1}$, $\nu_{2}$, $l_{1}$, $l_{2}$ at 374.5, 340, 64, and 122 cm\textsuperscript{-1} respectively, and a broad peak $\nu_{4}$ at 320 cm\textsuperscript{-1}. Peaks between 200, and 400 cm\textsuperscript{-1} refer to (Sb, As)S\textsubscript{3} groups modes\cite{Kharbish2007}.
Position of $\nu_{3}$ was found by the spectra fitting.
The fit result is presented in Figure~\ref{fig:full_raman}, and in Table 3. Peaks below 200 cm\textsuperscript{-1} are related to the lattice dynamics\cite{Buzatu2017}.

\begin{figure}[h]
\centering
\includegraphics[width=0.48\textwidth]{raman_25_CuAsS3_eng_components}
\caption{\label{fig:full_raman} The Raman spectrum of the crystalline tennantite. Peaks between 200, and 400 cm\textsuperscript{-1} refer to (Sb, As)S\textsubscript{3} groups modes\cite{Kharbish2007}. Peaks below 200 cm\textsuperscript{-1} are related to the lattice dynamics\cite{Buzatu2017}. Blue --- experimental data, red --- the superposition of modes, dotted --- fitted peaks}.
\end{figure}

Those modes were observed in tetrahedrites\cite{May2016}, and it was noted that they were caused by strongly anharmonic vibrations of the trigonally-bonded Cu atoms.
Within this approach, the Einstein solid model is used to describe independent harmonic oscillators.
If so, the low energy spectrum should consist of peaks with the Einstein's energies, which we found by DebyeFit (Table~\ref{tab:enst_temp}).
A results of calculations are presented in Figure~\ref{fig:low_energ_raman}.
The Einstein's energies from structural study were used as the initial points for the fit, and in Table~\ref{tab:ram_fit} the initial  and fitted wavenumbers are presented.
The low energy $l_{1}$ and $l_{2}$ peaks are well described by Einstein's energies of Cu2, Cu21, Cu1, and As (66, 40, 79, and 122 cm\textsuperscript{-1} respectively).
Thus, the reasons for the strong anharmonic behavior, described in the papers, is a dynamic disorder of the copper atoms. Moreover, arsenic atoms are shifted by the copper atoms.
Consequently, this leads to out-of-plane low frequency rattling modes, and a low lattice thermal conductivity.

\begin{table}
\caption{\label{tab:ram_fit}
Initial and fitted Einstein's energies. Initial energies are Einstein's energies from structural study.}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{ccccc}
&
\textrm{ Cu2   }&
\textrm{ Cu21  }&
\textrm{ Cu1     }&
\textrm{ As    } \\

Initial Einstein's energies, cm\textsuperscript{-1}	  &  72  & 51	& 80 & 129  \\
Fitted Einstein's energies, cm\textsuperscript{-1}	  &  66  & 40	& 79 & 122  \\

\end{tabular}}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{raman_25_CuAsS3_low_energy}
\caption{\label{fig:low_energ_raman} The Raman spectrum of the tennantite crystal  below 200 cm\textsuperscript{-1}. Experimental peaks are considered as the peaks with Einstein's energies. Blue --- experimental data, red --- modes based on the Einstein's energies fit, dotted --- fitted peaks.}
\end{figure}

\subsection{Theoretical analysis of possible polytypes and morphology of Laves polyhedra }\label{sec:level2}

Using the DFT calculations, we tested an assumption that the synthetic tennantite crystal structure is not the most energetically stable, and could  feature various polytypes.
As an initial point, we considered tennantite structure described in  \hmn{I -4 2 m}\ space group (henceforth called {\it reference structure}).
The unit cell contains Laves polyhedron formed by copper atoms around sulfur ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
By shifting copper atoms by ca. 1~$\angstrom$, we produced a population of structures with varying shapes of Laves polyhedra, which were then subjected to the procedure of unconstrained structural optimization.
The Laves polyhedra morphologies before, and after the optimization, are shown in Figure~\ref{fig:init_and_opt_laves}.
The total energy differences between the initial tennantite and optimized structures are shown in Figure~\ref{fig:energy_structure_rescale}.

\begin{figure}
\centering
 \includegraphics[width=0.48\textwidth]{Init_and_opt_renamed}
 \caption{\label{fig:init_and_opt_laves} Geometries of SCu\textsubscript{6} Laves polyhedra before, and after structural optimization. Sulfur atoms are shown in yellow, copper atoms before optimization are shown in grey, and after optimization in blue. VESTA\cite{Momma2011} was used for visualisation. }
\end{figure}

Our calculations show, that the experimentally determined synthetic tennantite structure is not the most energy favorable one at 0~K.

We observe 8 structures in our population with the energies less than the starting one.
They correspond to the structures No's 2, 3, 9, 11, 14, 17, 18, and 19, with the last one  possessing the the lowest energy.
The coordination of the central sulfur atom deviates quite a lot from an ideal octahedral, with the energy gain being achieved by shifting one (structure 9), two (structures 17, 18), or three (structures 2, 3, 11, 14, 19) atoms.

%\begin{table}[h]%The best place to locate the table environment is directly after its first reference in text
%\caption{\label{tab:energy}%
%Anisotropic extinction parameters in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
%}
%\begin{ruledtabular}
%\begin{tabular}{cccc}
%Structure, number & Energy. eV & Structure, number & Energy, eV \\
%\colrule
%0   &   0.00 & 10   &  0.16 \\
%1   &   0.23 & 11   & -0.02 \\
%2   &  -0.02 & 12   &  0.05 \\
%3   &  -0.02 & 13   &  0.03 \\
%4   &   0.05 & 14   & -0.02 \\
%5   &   0.13 & 15   &  0.02 \\
%6   &  -0.00 & 16   &  0.12 \\
%7   &   0.23 & 17   & -0.02 \\
%8   &   0.06 & 18   & -0.03 \\
%9   &  -0.01 & 19   & -0.04 \\
%
%\end{tabular}
%\end{ruledtabular}
%\end{table}

\begin{table*}
\caption{\label{tab:energy}%
The difference between the reference structure energy, and the unit cell energy of tennantite with different Laves polyhedron.
}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{ccccccccccc}
Structure, number & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
The difference of unit cells energies, eV &  0.00 &  0.23 & -0.02 & -0.02 &  0.05 &  0.13 & -0.00 &  0.23 &  0.06 & -0.01 \\
 \\
Structure, number & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 \\
The difference of unit cells energies, eV &  0.16 & -0.02 &  0.05 &  0.03 & -0.02 &  0.02 &  0.12 & -0.02 & -0.03 & -0.04  \\
\end{tabular}}
\end{table*}

The analysis  of atomic charge distribution shows that the optimized structures can be divided into three groups: 1) with As charge of ca. $+3$ (reference compound also falls into this category), 2) with As charge less than $+1$, and 3) with intermediate As charge (between ca. $+1$ and $+2$).
Charge density on arsenic affects substantially the respective charge density at 1st sulfur position (see~Appendix), and has a minor effect on Cu2 charges, while Cu1 is virtually unaffected by any change.
The other sulfur atom shows minor charge fluctuations, and they appear to be not directly associated with the state of arsenic.

\begin{figure}
\centering
 \includegraphics[width=0.48\textwidth]{energy_structure_rescale_ri}
 \caption{\label{fig:energy_structure_rescale} The difference between the reference structure energy and the unit cell energy of tennantite with different Laves polyhedron. Horizontal red line shows the reference unit cell energy. }
\end{figure}

Each of these groups has structures with an energy gain over the reference structure, and each of them has a certain split of a positive charge on Cu2 atoms, while Cu1 atomic charges remain constant throughout.
Thus, we can say that the splitting of the Cu2 position into Cu2 and Cu21, as evident from the XRD structure analysis, facilitates the differences in charge distribution.
Hence, the energy gain from forming Cu21 position leads to slightly different electronic states of Cu2 and Cu21 atoms, which, in turn, leads to the formation of asymmetric bonds, as was pointed out for tetrahedrites\cite{Lai2015,Long2020}.
We can also observe certain similarities between tennantite and inorganic compounds featuring atoms with  {\it 3d\textsuperscript{9}}  configuration, and having asymmetric Fermi surface.
The resulting complex charge distribution, and variances in the copper atom states, may, in turn, be the reason for complex exchange interactions and the reported antiferromagnetic ordering\cite{yaroslavzev2019} in tennantite.
Moreover, the same structure features have been described in tetrahedrite\cite{DiPaola2020}.
Authors noted, that understanding these features provides descriptions of the phonon-limited electrical resistivity, and the Lorenz number.

It must be noted that the majority of the favorable structures belongs to group 2, i.e. more covalent structures with both arsenic and sulfur atoms showing the relatively low positive and negative charges, respectively.
Interestingly, the reference structure is significantly more ionic in this respect.
Also, we must point out that, according to the DFT calculations, several structures have energy minimum within hundredths of eV (Table~\ref{tab:energy}), i.e. only several~kJ/mol (1~eV~$\sim$~96.5 kJ/mol), which is on the limit of the accuracy of the method.
This indicates, that the tennantite experimental structure may be a mean result of several variations of the copper atoms shifts.

\section{Conclusions}\label{sec:level1}
In conclusion, the structural variety of synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13},  leads to  a dynamic disorder of the copper atoms, asymmetric bonds, and inconsistent electronic densities.
This brings to the out-of-plane low frequency rattling modes, well described by Einstein characteristic temperatures: 74, 104, 115, and 185~K.
The peculiarities of the tennantite crystal and electronic structures lead to asymmetric Fermi surface, thus makinkg tennantite--tetrahedrite group compounds attractive research objects.

Our extensive structural studies revealed a strong electron density anisotropy of the bulk sample, with no evidence of a distortion or local defects.

The specially-designed  technique was tested for the experimental ADPs analysis, and we have demonstrated a new method of the experimental study of a crystal structure and its Brillouin zone.

\section{Acknowledgments}\label{sec:level1}
This research was partially supported by Russian Science Foundation (Grant No. 19-13-00451). The calculations were carried out using the equipment of the shared research facilities of the HPC computing resources at Lomonosov Moscow State University.
X-ray diffraction study was performed using the equipment of the Shared Research Center FSRC “Crystallography and Photonics” RAS and was supported by the Ministry of  Science and Higher Education of the Russian Federation (project RFMEFI62119X0035). X-ray diffraction part of this work was supported by the Ministry of Science and Higher Education of the Russian Federation within the State assignment  of the Federal Scientific Research Center “Crystallography and Photonics” of the Russian Academy of Sciences.
Electron microscopy was carried out using the equipment of the Resource Centre “Nanozond“
National Research Center “Kurchatov Institute“.
We thank I. A. Perezhogin for valuable comments and  Professor A. N. Babushkin for the tennantit ingot.

\section{References}\label{sec:level1}
\bibliographystyle{elsarticle-num}
\bibliography{reff}

\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2021-01-16 SM/paper_tennantite.tex
Interatomic distances and Summary of crystallographic information tables changed

@@
 Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
-Cu1 -- S1$\times$4   & 2.3177(17) & 2.315511)  & 2.3099(6) \\
-Cu2 -- Cu21$\times$2 & 0.92(2)    & 0.891(11)  & 0.95(3) \\
-Cu2 -- S1$\times$2   & 2.215(4)   & 2.211(3)   & 2.219(3) \\
-Cu2 -- S2            & 2.212(7)   & 2.224(4)   & 2.206(5) \\
-Cu21 -- S1$\times$2  & 2.421(18)  & 2.427(11)  & 2.427(17) \\
-Cu21 -- S2           & 2.356(15)  & 2.326(11)  & 2.380(14) \\
-As1 -- S1$\times$3   & 2.2505(18) & 2.2503(12) & 2.2457(19) \\
-Cu21 -- As1          & 2.58(2)    & 2.604(11)  & 2.535(19) \\
-Cu2 -- As1           & 3.4832(11) & 3.4816(7)  & 3.480(4) \\
+Cu1 -- S1$\times$4   & 2.3177(17) & 2.3147(10) & 2.3099(6) \\
+Cu2 -- Cu21$\times$2 & 0.890(17)  & 0.868(9)   & 0.95(3) \\
+Cu2 -- S1$\times$2   & 2.208(4)   & 2.211(3)   & 2.219(3) \\
+Cu2 -- S2            & 2.219(6)   & 2.223(4)   & 2.206(5) \\
+Cu21 -- S1$\times$2  & 2.421(18)  & 2.420(10)  & 2.427(17) \\
+Cu21 -- S2           & 2.326(15)  & 2.316(10)  & 2.380(14) \\
+As1 -- S1$\times$3   & 2.2543(19) & 2.2530(10) & 2.2457(19) \\
+Cu21 -- As1          & 2.604(17)  & 2.626(10)  & 2.535(19) \\
+Cu2 -- As1           & 3.4816(11) & 3.4813(7)  & 3.480(4) \\
 
@@
 V, \AA\textsuperscript{3}                                  & \multicolumn{2}{c}{1053.19(4)}	                              	             & 1047.91(4)	\\
-S.G.                                                       & \multicolumn{3}{c}{1053.19(4)}	                                             	\\
+S.G.                                                       & \multicolumn{3}{c}{ \hmn{I -4 3 m} }	                                             	\\
 Radiation, wavelength (\AA)                                & \multicolumn{2}{c}{Ag K\textsubscript{$\alpha$}, 0.56089}		                & Mo K\textsubscript{$\alpha$}, 0.71069	\\
@@
 Absorption correction                                      & \multicolumn{2}{c}{Analytical (sphere)}	                    	             & Analytical (crystal shape)	\\
-q\textsubscript{max}, deg.                                 & \multicolumn{2}{c}{29.85}	                                  	             & 42.08	\\
-R\textsubscript{int}                                       & 0.041	                                                     & ---	         & 0.049	\\
+$\Theta$\textsubscript{max}, deg.                                 & \multicolumn{2}{c}{29.85}	                                  	             & 42.08	\\
+R\textsubscript{int}                                       & 0.046	                                                     & ---	         & 0.049	\\
 N\textsubscript{ref} , collected                           & \multicolumn{2}{c}{3509}	                                    	             & 11026	\\
-N\textsubscript{ref} , independent, $I\geqslant2\sigma(I)$ & 553	                                                       & 2840	         & 667	\\
+N\textsubscript{ref} , independent, $I\geqslant2\sigma(I)$ & 570	                                                       & 2837	         & 667	\\
 N\textsubscript{paf}                                       & 50	                                                         & 55	           & 44	\\
-Refinement on                                              & \multicolumn{2}{c}{$|F|^2$}	                                	             & $|F|$	\\
+Refinement on                                              & \multicolumn{2}{c}{$|F|$}	                                	             & $|F|$	\\
 Anharmonic, Atoms (rank)                                   & \multicolumn{2}{c}{Cu1(4), Cu2(3), Cu21(3), S1(3), As1(3)}	  	             & Cu1(4), Cu2(3), Cu21(3), S2(4)	\\
 GOF                                                        & 1.01	                                                       & 1.04	         & 1.00	\\
-R/{\it w}R\textsubscript{2}                                & 0.025/0.066	                                               & 0.038/0.098	 & 0.029/0.038	\\
-Min. Negative JPDF, \% of positive                         & -2.7	                                                       & 	             & -3.4	\\
-$\pm\Delta\rho$, {\it e}\AA\textsuperscript{-3}            & +0.7/–0.63	                                                 & +0.95/–1.32	 & +1.7/–1.2	\\
+R/{\it w}R\textsubscript{2}                                & 0.028/0.036	                                               & 0.038/0.050	 & 0.029/0.038	\\
+Min. Negative JPDF, \% of positive                         & -2.7	                                                       & 	-3.8             & -3.4	\\
+$\pm\Delta\rho$, {\it e}\AA\textsuperscript{-3}            & +0.64/–0.76	                                                 & +1.18/–0.61	 & +1.7/–1.2	\\
 

### 2021-01-16 SM/paper_tennantite.tex
Refined atomic parameters and refined anisotropic ADP added

@@
 Table~\ref{tab:inter_dist} and in~Table~\ref{tab:crystallographic_information} show the~comparison of previous results\cite{yaroslavzev2019} and the spherical shape single-crystal structural data.
+Refined atomic parameters and refined anisotropic ADP are presented in~Table~\ref{tab:atom_param} and in~Table~\ref{tab:ref_adp}.
 
@@
 \end{table*}
+
+\begin{table}
+\caption{\label{tab:atom_param}
+Refined atomic parameters in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}. 
+Cu(1): $\frac{1}{2}$,$\frac{1}{4}$,0; Cu(2): x,0,0; Cu(21): x,y,y; As(1): x,x,x;  S(1): x,y,–y; S(2): 0,0,0.}
+\centering
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{lccc}
+&
+Averaged, \AA  &
+Extinct, \AA  &
+Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
+Occupancy, Cu(2)                          & 0.660(8)    & 0.670(5)     & 0.679(11)  \\
+x, Cu(2)                                  & 0.2181(6)   & 0.2185(4)    & 0.2172(5)  \\
+x, Cu(21)                                 & 0.2113(15)  & 0.2111(10)   & 0.2149(12) \\
+y, Cu(21)                                 & 0.0617(17)  & 0.0601(9)    & 0.0662(19) \\
+x, As(1)                                  & 0.24141(10) & 0.24141(6)   & 0.24162(4) \\
+x, S(1)                                   & 0.3566(2)   & 0.35709(12)  & 0.35722(7) \\
+–y, S(1)                                  & 0.11809(14) & 0.11835(8)   & 0.11854(6) \\
+Ueq$\times$10\textsuperscript{4}, Cu(1)   & 212(3)      & 214(2)       & 184(3)     \\
+Ueq$\times$10\textsuperscript{4}, Cu(2)   & 399(8)      & 415(5)       & 339(5)     \\
+Ueq$\times$10\textsuperscript{4}, Cu(21)  & 543(22)     & 573(13)      & 420(3)     \\
+Ueq$\times$10\textsuperscript{4}, As(1)   & 146.8(5)    & 147.1(3)     & 114.0(7)   \\
+Ueq$\times$10\textsuperscript{4}, S(1)    & 151.6(15)   & 152.5(10)    & 111.0(13)  \\
+Ueq$\times$10\textsuperscript{4}, S(2)    & 164.6(14)   & 167.5(9)     & 160(7)     \\
+
+\end{tabular}
+}
+\end{table}
+
+\begin{table}
+\caption{\label{tab:ref_adp}
+Refined anisotropic ADP in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.}
+\centering
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{lccc}
+&
+Averaged, \AA  &
+Extinct, \AA  &
+Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
+$U_{11}$, $U_{33}\times$10\textsuperscript{4}, Cu(1)             & 176(4)      & 179(3)     & 146(3)  \\
+$U_{22}\times$10\textsuperscript{4}, Cu(1)                       & 284(9)      & 284(6)     & 248(7)  \\
+$U_{11}\times$10\textsuperscript{4}, Cu(2)                       & 158(7)      & 148(9)     & 117(6)  \\
+$U_{22}$, $U_{33}\times$10\textsuperscript{4}, Cu(2)             & 493(14)     & 537(14)    & 451(9)  \\
+$U_{11}\times$10\textsuperscript{4}, Cu(21)                      & 210(20)     & 193(20)    & 205(18)  \\
+$U_{22}$, $U_{33}\times$10\textsuperscript{4}, Cu(21)            & 660(70)     & 710(40)    & 490(60)  \\
+$U_{12}$, $U_{13}\times$10\textsuperscript{4}, Cu(21)            & –140(40)    & –70(30)    & –170(30)  \\
+$U_{23}\times$10\textsuperscript{4}, Cu(21)                      & 470(80)     & 530(50)    & 290(60)  \\
+$U_{11}\times$10\textsuperscript{4}, S(1)                        & 134(4)      & 133(3)     & 90(3)  \\
+$U_{22}$, $U_{33}\times$10\textsuperscript{4}, S(1)              & 163(2)      & 163.2(16)  & 119.9(18)  \\
+$U_{12}$, $-U_{13}\times$10\textsuperscript{4}, S(1)             & –19.7(18)   & –22.0(14)  & –23.6(14)  \\
+$U_{23}\times$10\textsuperscript{4}, S(1)                        & 2(3)        & 3(2)       & –8(2)  \\
+$U_{11}$, $U_{22}$, $U_{33}\times$10\textsuperscript{4}, S(2)    & 166(4)      & 169(3)     & 128(3)  \\
+$U_{11}$, $U_{22}$, $U_{33}\times$10\textsuperscript{4}, As(1)   & 151.9(15)   & 149.0(11)  & 112.8(13)  \\
+$U_{12}$, $U_{13}$, $U_{23}\times$10\textsuperscript{4}, As(1)   & 1.4(12)     & 0.1(9)     & –1.6(10)  \\
+
+\end{tabular}
+}
+\end{table}
 

### 2021-01-17 paper_tennantite.tex

@@
 \subsection{Single-crystal X-ray diffraction}\label{sec:level2}
-A spherical shape single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study.
+A spherical shape single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study\cite{Becker1975}.
 Enraf-Nonius CAD-4 diffractometer with AgK\textsubscript{$\alpha$} and graphite monochromator was used. 
@@
 Neither XRD, nor TEM data shown defects.
-Due to the crystal growth method used, we suspected a possibility of anisotropic extinction.
-The intensity vs  $\psi$ angle were measured for several reflections to analyze this effect.
-
-The results are presented in Fig.~\ref{fig:rock_curv} .
-All curves were approximated by the least-square fitting.
-Only for \hkl[4 0 0], \hkl[0 4 0], and \hkl[0 0 4] reflections the coefficients with $x$ and $x^{2}$ were in the range of 5--8$\sigma$, while for the two other sets they were about $\sigma$ or less (with one 2$\sigma$ exception).
-Thus, we conclude that the intensities of weak reflections at small angles and reflections at high angles have fixed $\psi$ angles.
-On the contrary, $\psi$ angles of strong reflections with small $\sin\theta/\lambda$ vary, that may indicate an anisotropic extinction.
-
-\begin{figure*}
-\centering
-\subfigure{\includegraphics[width=0.3\textwidth]{200}}
- \quad
-\subfigure{\includegraphics[width=0.3\textwidth]{400}}
- \quad
-\subfigure{\includegraphics[width=0.3\textwidth]{1200}}
-\caption{\label{fig:rock_curv} Normalized intensities of reflections vs.
-$\psi$ angle; left --- 200, 020, 002 (weak, sin=0.098), middle --- 400, 040, 004 (strong, sin=0.197), right --- 1200, 0120, 0012 (moderate, sin=0.590).}
-\end{figure*}
 
@@
 
-The extinction can be explained by the dynamic disorder of Cu21 atoms. Such a disorder is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
+Due to the crystal growth method used, anisotropic extinction in the sample takes place. Extinction parameters are presented in the Table~\ref{tab:anis_ext}.
+Also the extinction can be explained by the dynamic disorder of Cu21 atoms. Such a disorder is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
 The electron diffraction, and overlay of HAADF image with the tennantite crystal [110] zone generated by VESTA\cite{Momma2011}, are shown in Appendix.

### 2021-01-21 paper_tennantite.tex
text fixed based on comments

@@
 \begin{abstract}
-Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedride group of minerals with a low lattice thermal conductivity.
+Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedride group with a low lattice thermal conductivity.
 The atomic displacement parameters and low-energy optical phonon modes are discussed within the context of the structure variations and percularities of the charge distributions.
@@
 
-The tennantite-tetrahedride group of minerals represents a large class of inorganic compounds including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
+The tennantite-tetrahedride group represents a large class of inorganic compounds including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
 
@@
 
-Some authors note\cite{DiBenedetto2005,Tanaka2015}, that asymmetric bonds give rise to magnetic properties and, in some cases, to antiferromagnetic ordering\cite{yaroslavzev2019,Blandy_2018}.
+Some authors note\cite{DiBenedetto2005,Tanaka2015}, that asymmetric bonds give rise to magnetic properties and, in some cases, to antiferromagnetic (AFM) ordering\cite{yaroslavzev2019,Blandy_2018}.
 In both kinds of materials, deviations from the Curie-Weiss law in the temperature dependencies of the magnetization were revealed: at 124~K\cite{Hathwar2019} in tennantite, and at 84~K\cite{Nasonova2016_2} in tetrahedrite.
@@
 This effect is accompanied by As1 and S2 atoms displacement, which was also observed in ref.~ \cite{Hathwar2019}.
-We also investigated the low- and room-temperature electronic structures of a synthetic tennantite based on the DFT calculations, which confirmed the second-order transition from the low-temperature AFM state to the room-temperature PM state\cite{yaroslavzev2019}.
+We also investigated the low- and room-temperature electronic structures of a synthetic tennantite based on the DFT calculations, which confirmed the second-order transition from the low-temperature AFM to the room-temperature PM state\cite{yaroslavzev2019}.
 
@@
 High quality single crystals of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} for the XRD analysis were grown using a two-step procedure.
-At first, bulk Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} has been prepared by a high-temperature technique from copper (99.5~\%), arsenic (99.5~\%), and sulfur (99.5~\%).
+At first, bulk Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} has been prepared by a high-temperature technique from copper (99.5~\%), arsenic (99.5~\%), and sulpher (99.5~\%).
 Then, the ingots were subjected to directional recrystallization by the Bridgman-Stockbarger technique in a two-zone furnace.
@@
 Enraf-Nonius CAD-4 diffractometer with AgK\textsubscript{$\alpha$} and graphite monochromator was used.
-The spherical shape single-crystal structural study results are presented in Appendix, they are compared with the structural data of the irregular form sample\cite{yaroslavzev2019}.
+The spherical shape single-crystal structural study results are presented in Appendix, they are compared with the structural data of the \textcolor{red}{polyhedra} defined form sample\cite{yaroslavzev2019}.
 
@@
 Study of the high-grade single crystal allowed us to re-investigate the crystal structure of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  with a high precision.
+\textcolor{red}{The structure was refined in a way similar to described early\cite{yaroslavzev2019}.
+The sum of occupancies for Cu2, Cu21 and its symmetry related site were constrained to 1.
+Due to rather large distance between these atoms their ADP were refined independently.
+The maximum entropy method (MEM) refinement gave the result identical to \cite{yaroslavzev2019}.}
 Our data confirms that the compound contains 12 copper atoms per formula unit, and shows no evidences of a copper deficiency.
@@
 Due to the crystal growth method used, anisotropic extinction in the sample takes place. Extinction parameters are presented in the Table~\ref{tab:anis_ext}.
-Also the extinction can be explained by the dynamic disorder of Cu21 atoms. Such a disorder is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
+\textcolor{red}{The disorder of Cu21} is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
 The electron diffraction, and overlay of HAADF image with the tennantite crystal [110] zone generated by VESTA\cite{Momma2011}, are shown in Appendix.
@@
 If so, the low energy spectrum should consist of peaks with the Einstein's energies, which we found by DebyeFit (Table~\ref{tab:enst_temp}).
-A results of calculations are presented in Figure~\ref{fig:low_energ_raman}.
+Results of calculations are presented in Figure~\ref{fig:low_energ_raman}.
 The Einstein's energies from structural study were used as the initial points for the fit, and in Table~\ref{tab:ram_fit} the initial  and fitted wavenumbers are presented.
@@
 As an initial point, we considered tennantite structure described in  \hmn{I -4 2 m}\ space group (henceforth called {\it reference structure}).
-The unit cell contains Laves polyhedron formed by copper atoms around sulfur ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
+The unit cell contains Laves polyhedron formed by copper atoms around sulpher ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
 By shifting copper atoms by ca.
@@
  \caption{\label{fig:init_and_opt_laves} Geometries of SCu\textsubscript{6} Laves polyhedra before, and after structural optimization.
-Sulfur atoms are shown in yellow, copper atoms before optimization are shown in grey, and after optimization in blue.
+Sulpher atoms are shown in yellow, copper atoms before optimization are shown in grey, and after optimization in blue.
 VESTA\cite{Momma2011} was used for visualisation.
@@
 They correspond to the structures No's 2, 3, 9, 11, 14, 17, 18, and 19, with the last one  possessing the the lowest energy.
-The coordination of the central sulfur atom deviates quite a lot from an ideal octahedral, with the energy gain being achieved by shifting one (structure 9), two (structures 17, 18), or three (structures 2, 3, 11, 14, 19) atoms.
+The coordination of the central sulpher atom deviates quite a lot from an ideal octahedral, with the energy gain being achieved by shifting one (structure 9), two (structures 17, 18), or three (structures 2, 3, 11, 14, 19) atoms.
 
@@
 $+1$ and $+2$).
-Charge density on arsenic affects substantially the respective charge density at 1st sulfur position (see~Appendix), and has a minor effect on Cu2 charges, while Cu1 is virtually unaffected by any change.
-The other sulfur atom shows minor charge fluctuations, and they appear to be not directly associated with the state of arsenic.
+Charge density on arsenic affects substantially the respective charge density at 1st sulpher position (see~Appendix), and has a minor effect on Cu2 charges, while Cu1 is virtually unaffected by any change.
+The other sulpher atom shows minor charge fluctuations, and they appear to be not directly associated with the state of arsenic.
 
@@
 We can also observe certain similarities between tennantite and inorganic compounds featuring atoms with  {\it 3d\textsuperscript{9}}  configuration, and having asymmetric Fermi surface.
-The resulting complex charge distribution, and variances in the copper atom states, may, in turn, be the reason for complex exchange interactions and the reported antiferromagnetic ordering\cite{yaroslavzev2019} in tennantite.
+The resulting complex charge distribution, and variances in the copper atom states, may, in turn, be the reason for complex exchange interactions and the reported AFM ordering\cite{yaroslavzev2019} in tennantite.
 Moreover, the same structure features have been described in tetrahedrite\cite{DiPaola2020}.
@@
 It must be noted that the majority of the favorable structures belongs to group 2, i.e.
-more covalent structures with both arsenic and sulfur atoms showing the relatively low positive and negative charges, respectively.
+more covalent structures with both arsenic and sulpher atoms showing the relatively low positive and negative charges, respectively.
 Interestingly, the reference structure is significantly more ionic in this respect.

### 2021-01-24 paper_tennantite.tex

@@
 %% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+% \documentclass[final,1p,times,twocolumn]{elsarticle}
 %% \documentclass[final,3p,times]{elsarticle}
@@
 The tennantite-tetrahedride group represents a large class of inorganic compounds including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
-
 Despite being known for over two centuries, these minerals are still under investigation, both due to  structural peculiarities and potential applications.
 Arsenic- and antimony-containing compounds of this class are the advanced thermoelectric materials with a low lattice thermal conductivity\cite{Sootsman2009,Chetty2015}.
-Understanding the relationships between the crystal structure and phonon propagation, and scattering, is of a prime importance for designing new thermoelectric materials.
 
+\textcolor{red}{The tennantite structure treated as sphalerite-type and belongs to \hmn{I -4 3 m} space group\cite{yaroslavzev2019,Makovicky_2006}.
+There are three copper position: Cu1 is tetrahedrally coordinated by four sulpfur atoms, Cu2 is coordinated by three sulpfur atoms and Cu21 is tetrahedrally coordinated by three sulpfur and arsenic atoms.
+Cu21 and Cu2 atoms possess very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view} right).}
 In a case of tennantite- and tetrahedrite-based materials, it is generally considered, that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen p orbitals\cite{Lai2015}.
 Such a hybridization leads to a bonding asymmetry, and out-of-plane low frequency rattling modes, which are quasi-localized and anharmonic\cite{May2016,Bouyrie2015}.
+
+\begin{figure}[ht]
+\centering
+\subfigure{\includegraphics[width=0.4\columnwidth]{general_view}}
+ \quad
+\subfigure{\includegraphics[width=0.35\columnwidth]{general_view_laves}}
+\caption{\label{fig:generel_view} \textcolor{red}{Left --- the view of the Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} tennantite structure and of coordination polyhedra around the Cu1 (blue) and the Laves polyhedra (yellow); right --- the Laves polyhedra with Cu2 and Cu21 atoms with occupancy.} }
+\end{figure}
 

### 2021-01-24 paper_tennantite.tex
comment added

@@
 
-\title{Laves polyhedrons in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and the lattice dynamics}
+\title{Laves polyhedra in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and its lattice dynamics}
 
@@
 Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedride group with a low lattice thermal conductivity.
-The atomic displacement parameters and low-energy optical phonon modes are discussed within the context of the structure variations and percularities of the charge distributions.
-The latter indicates that the tennantite structure tends to conform to the covalent, asymmetric bonds and inconsistent electronic densities.
-Accoding to the DFT calculations results, varying shifts of copper atoms in Laves polyhedron are featured in the unit cells with very close total energies with deviation less than 0.24~eV, which can explain the observed behavior of the atomic displacement parameters.
+\textcolor{red}{Combined data from high-quality X-ray diffraction, electron microscopy (STEM--HAADF), Raman spectroscopy, as well as DFT calculations are used to analyze the peculiarities of structure stability and dynamics.
+A atomic displacement parameters and low-energy optical phonon modes are discussed within the context of the structure variations and pecularities of the charge distributions.
+The latter indicates that the tennantite structure tends to conform to the covalent polar bonds and its charge distribution significantly affected by the atomic shifts in Laves polyhedra.
+According to the DFT calculations, there is a population of stable model structures with varying shifts of copper atoms in Laves polyhedra, with total energies being very close (within 0.24~eV), which can explain the observed behavior of the atomic displacement parameters.}
 A specially designed  technique used for the experimental analysis of the atomic displacement parameters  revealed Einstein characteristic temperatures in the tennantite structure to be in the range of 50--190~K, attributed to  low-energy optical phonon modes.
@@
 \begin{itemize}
-  \item Synthetic tennantite Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} structure consists of disordered Laves polygons
-  \item DFT calculations reveal a mixed valence of Cu atoms, and Laves polygon distortions
+  \item Synthetic tennantite Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} structure consists of disordered Laves \textcolor{red}{polyhedra}
+  \item DFT calculations reveal a mixed valence of Cu atoms, and Laves \textcolor{red}{polyhedra} distortions
   \item Jahn-Teller distortions give rise to a set of unit cells with close ground energies
-  \item Rattling vibration modes refer to Einstein’s temperatures of 74, 104, 115, 185K
+  \item Rattling vibration modes refer to Einstein temperatures of 74, 104, 115, 185K
 \end{itemize}
@@
 thermoelectic materials\sep
+DFT\sep
 anisotropy\sep
@@
 Cu21 and Cu2 atoms possess very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view} right).}
-In a case of tennantite- and tetrahedrite-based materials, it is generally considered, that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen p orbitals\cite{Lai2015}.
+In a case of tennantite- and tetrahedrite-based materials, it is generally considered, that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen \textcolor{red}{{\it p}} orbitals\cite{Lai2015}.
 Such a hybridization leads to a bonding asymmetry, and out-of-plane low frequency rattling modes, which are quasi-localized and anharmonic\cite{May2016,Bouyrie2015}.
@@
 
-However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves polyhedra in the structure, were left aside in the previous paper\cite{yaroslavzev2019}.
+However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves \textcolor{red}{polyhedra} in the structure, were left aside in the previous paper\cite{yaroslavzev2019}.
 In this paper, we focus on these problems, and  investigate the tennantite cell energy distribution, and the charge density differences for different Cu positions in Cu$_{6}^{II}$S$^{II}$.
@@
 Enraf-Nonius CAD-4 diffractometer with AgK\textsubscript{$\alpha$} and graphite monochromator was used.
-The spherical shape single-crystal structural study results are presented in Appendix, they are compared with the structural data of the \textcolor{red}{polyhedra} defined form sample\cite{yaroslavzev2019}.
+The spherical shape single-crystal structural study results are presented in Appendix, they are compared with the structural data \textcolor{red}{from} the \textcolor{red}{polyhedra} defined form sample\cite{yaroslavzev2019}.
 
@@
 
-\section{Result and discussion}\label{sec:level1}
+\section{Results and discussion}\label{sec:level1}
 
@@
 Our data confirms that the compound contains 12 copper atoms per formula unit, and shows no evidences of a copper deficiency.
-Neither XRD, nor TEM data shown defects.
+Neither XRD, nor TEM data \textcolor{red}{have shown detectable packing defects}.
 
@@
 
-\subsection{Theoretical analysis of possible polytypes and morphology of Laves polyhedra }\label{sec:level2}
+\subsection{Theoretical analysis of possible polytypes and morphology of Laves \textcolor{red}{polyhedra} }\label{sec:level2}
 
@@
 As an initial point, we considered tennantite structure described in  \hmn{I -4 2 m}\ space group (henceforth called {\it reference structure}).
-The unit cell contains Laves polyhedron formed by copper atoms around sulpher ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
+The unit cell contains Laves \textcolor{red}{polyhedra} formed by copper atoms around sulpher ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
 By shifting copper atoms by ca.
-1~$\angstrom$, we produced a population of structures with varying shapes of Laves polyhedra, which were then subjected to the procedure of unconstrained structural optimization.
-The Laves polyhedra morphologies before, and after the optimization, are shown in Figure~\ref{fig:init_and_opt_laves}.
+1~$\angstrom$, we produced a population of structures with varying shapes of Laves \textcolor{red}{polyhedra}, which were then subjected to the procedure of unconstrained structural optimization.
+The Laves \textcolor{red}{polyhedra} morphologies before, and after the optimization, are shown in Figure~\ref{fig:init_and_opt_laves}.
 The total energy differences between the initial tennantite and optimized structures are shown in Figure~\ref{fig:energy_structure_rescale}.
@@
  \includegraphics[width=0.48\textwidth]{Init_and_opt_renamed}
- \caption{\label{fig:init_and_opt_laves} Geometries of SCu\textsubscript{6} Laves polyhedra before, and after structural optimization.
+ \caption{\label{fig:init_and_opt_laves} Geometries of SCu\textsubscript{6} Laves \textcolor{red}{polyhedra} before, and after structural optimization.
 Sulpher atoms are shown in yellow, copper atoms before optimization are shown in grey, and after optimization in blue.
@@
 \caption{\label{tab:energy}%
-The difference between the reference structure energy, and the unit cell energy of tennantite with different Laves polyhedron.
+The difference between the reference structure energy, and the unit cell energy of tennantite with different Laves \textcolor{red}{polyhedra}.
 }
@@
  \includegraphics[width=0.48\textwidth]{energy_structure_rescale_ri}
- \caption{\label{fig:energy_structure_rescale} The difference between the reference structure energy and the unit cell energy of tennantite with different Laves polyhedron.
+ \caption{\label{fig:energy_structure_rescale} The difference between the reference structure energy and the unit cell energy of tennantite with different Laves \textcolor{red}{polyhedra}.
 Horizontal red line shows the reference unit cell energy.
@@
 The resulting complex charge distribution, and variances in the copper atom states, may, in turn, be the reason for complex exchange interactions and the reported AFM ordering\cite{yaroslavzev2019} in tennantite.
-Moreover, the same structure features have been described in tetrahedrite\cite{DiPaola2020}.
-Authors noted, that understanding these features provides descriptions of the phonon-limited electrical resistivity, and the Lorenz number.
+Moreover, the same structure features have been described for tetrahedrite\cite{DiPaola2020}.
+\textcolor{red}{The authors} noted, that understanding these features provides a key to descriptions of the phonon-limited electrical resistivity, and the Lorenz number.
 
@@
 only several~kJ/mol (1~eV~$\sim$~96.5 kJ/mol), which is on the limit of the accuracy of the method.
-This indicates, that the tennantite experimental structure may be a mean result of several variations of the copper atoms shifts.
+This indicates, that the tennantite experimental structure may be \textcolor{red}{an averaged} result of several variations of the copper atoms shifts.
 

### 2021-01-25 paper_tennantite.tex
minor improvnmets

@@
 \begin{abstract}
-Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedride group with a low lattice thermal conductivity.
+Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedri\textcolor{red}{t}e group with a low lattice thermal conductivity.
 \textcolor{red}{Combined data from high-quality X-ray diffraction, electron microscopy (STEM--HAADF), Raman spectroscopy, as well as DFT calculations are used to analyze the peculiarities of structure stability and dynamics.
@@
 
-The tennantite-tetrahedride group represents a large class of inorganic compounds including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
+The tennantite-tetrahedri\textcolor{red}{t}e group represents a large class of inorganic compounds including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
 Despite being known for over two centuries, these minerals are still under investigation, both due to  structural peculiarities and potential applications.
@@
 
-According to the structural study, these deviations take place due to the distortion of S\textsubscript{2}Cu\textsubscript{6} octahedra\cite{Tanaka2015}.
+According to the structural study, these deviations take place due to the distortion of \textcolor{red}{Cu\textsubscript{6}S} octahedra \textcolor{red}{(Laves polyhedra)}\cite{Tanaka2015}.
 The distortion at 84 K in tetrahedrite is reported to lead to either the symmetry lowering from \hmn{I -4 3 m} to \hmn{I -4 2 m}  space group accompanied by the displacement of S atoms\cite{Hathwar2019}, or to a shift of Cu2 atoms towards S\textsubscript{3} triangle plane with S\textsubscript{2} displacement\cite{Nasonova2016_2} in the same symmetry, and space group.
@@
 However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves \textcolor{red}{polyhedra} in the structure, were left aside in the previous paper\cite{yaroslavzev2019}.
-In this paper, we focus on these problems, and  investigate the tennantite cell energy distribution, and the charge density differences for different Cu positions in Cu$_{6}^{II}$S$^{II}$.
+In this paper, we focus on these problems, and  investigate the tennantite cell energy distribution, and the charge density differences for different Cu positions in Laves polyhedra.
 Also, we consider low-energy phonon modes, and peculiarities of the atomic displacement parameters in the temperature range of 85--293~K, the same as in Ref.~\cite{Dudka2019}, in a context of the cell energy distribution.
-To clarify distortions in Cu$_{6}^{II}$S$^{II}$ octahedra, a study of the spherical single-crystal sample was performed and  the high-angle annular dark-field (HAADF) image was obtained.
+To clarify distortions in Laves polyhedra, a study of the spherical single-crystal sample was performed and the high-angle annular dark-field (HAADF) image was obtained.
 
@@
 1~$\angstrom$, we produced a population of structures with varying shapes of Laves \textcolor{red}{polyhedra}, which were then subjected to the procedure of unconstrained structural optimization.
+\textcolor{red}{In the DFT calculations, where we cannot have Cu2 and Cu21 at the same time since we cannot have part of an atom occupying a position within a single polyhedron, we prefer to only use Cu2 notation, but distinguish their positions before and after optimization.}
 The Laves \textcolor{red}{polyhedra} morphologies before, and after the optimization, are shown in Figure~\ref{fig:init_and_opt_laves}.
@@
 
-The specially-designed  technique was tested for the experimental ADPs analysis, and we have demonstrated a new method of the experimental study of a crystal structure and its Brillouin zone.
+The specially-designed  technique was tested for the experimental ADPs analysis, and we have demonstrated a new method of the experimental study of a crystal structure.
 

### 2021-01-25 SM/paper_tennantite.tex

@@
 
-\title{Supplementary Material \--- Laves polyhedrons in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and the lattice dynamics}
+\title{Supplementary Material \--- Laves polyhedra in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and its lattice dynamics}
 
@@
 The calculation of integral intensities from diffraction patterns was performed using the CrysAlisPro program\cite{Rigaku}.
-The data processing included: consideration of geometric features of the data collection (Lorentz correction) and correction for polarization of radiation; calibration of the diffractometer\cite{Dudka2010}; absorption correction for polyhedron samples (performed by the Gaussian integration method\cite{Busing1957}); refinement of the half-wavelength contribution\cite{Dudka2010_2}; the correction for an extinction\cite{Becker1974}.
+The data processing included: consideration of geometric features of the data collection (Lorentz correction) and correction for polarization of radiation; calibration of the diffractometer\cite{Dudka2010}; absorption correction for \textcolor{red}{polyhedra} samples (performed by the Gaussian integration method\cite{Busing1957}); refinement of the half-wavelength contribution\cite{Dudka2010_2}; the correction for an extinction\cite{Becker1974}.
 The corrections and refinement of structural parameters were performed in the Jana2006\cite{Petek2014} and ASTRA programs\cite{Dudka2007}.

### 2021-01-26 paper_tennantite.tex
comparison added

@@
 Arsenic- and antimony-containing compounds of this class are the advanced thermoelectric materials with a low lattice thermal conductivity\cite{Sootsman2009,Chetty2015}.
+\textcolor{red}{For example, the studies of tetrahedrite doped with Mn, Fe, Co, Ni, Zn, Te, Se showed ZT values in the range from 0.2 to 1.13\cite{Heo2014,Suekuni2013,Lu2012,Barbier2016,Rout2020,Zhu2019}.}
 
@@
 There are three copper position: Cu1 is tetrahedrally coordinated by four sulpfur atoms, Cu2 is coordinated by three sulpfur atoms and Cu21 is tetrahedrally coordinated by three sulpfur and arsenic atoms.
+The one arsenic is coordinated by three sulpfur atoms.
 Cu21 and Cu2 atoms possess very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view} right).}
@@
 Some authors note\cite{DiBenedetto2005,Tanaka2015}, that asymmetric bonds give rise to magnetic properties and, in some cases, to antiferromagnetic (AFM) ordering\cite{yaroslavzev2019,Blandy_2018}.
-In both kinds of materials, deviations from the Curie-Weiss law in the temperature dependencies of the magnetization were revealed: at 124~K\cite{Hathwar2019} in tennantite, and at 84~K\cite{Nasonova2016_2} in tetrahedrite.
+In both kinds of materials, deviations from the Curie-Weiss law in the temperature dependencies of the magnetization were revealed: at 124~K\cite{Tanaka2015} in tennantite, and at 84~K\cite{Nasonova2016_2} in tetrahedrite.
 
@@
 Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) indicate the potential instability of this position. 
-Even after dividing Cu2 position into Cu2 and Cu21, the Cu2 position remains highly disordered.
+\textcolor{red}{According to structurel study of tennantie Cu2\cite{Hathwar2019} position may be describied as 6 differnt Cu position.
+But according our study even after dividing Cu2 position into Cu2 and Cu 21, the Cu2 position remains highly disordered and there are no reasons for adding additional positions.}
 This disordering is reliably described by the anharmonic model of atomic displacements using the Gram-Charlier expansion to the 4th order.
@@
 
-Those modes were observed in tetrahedrites\cite{May2016}, and it was noted that they were caused by strongly anharmonic vibrations of the trigonally-bonded Cu atoms.
-Within this approach, the Einstein solid model is used to describe independent harmonic oscillators.
+Within \textcolor{red}{approach above}, the Einstein solid model is used to describe independent harmonic oscillators.
 If so, the low energy spectrum should consist of peaks with the Einstein's energies, which we found by DebyeFit (Table~\ref{tab:enst_temp}).
@@
 The low energy $l_{1}$ and $l_{2}$ peaks are well described by Einstein's energies of Cu2, Cu21, Cu1, and As (66, 40, 79, and 122 cm\textsuperscript{-1} respectively).
-Thus, the reasons for the strong anharmonic behavior, described in the papers, is a dynamic disorder of the copper atoms. Moreover, arsenic atoms are shifted by the copper atoms.
+\textcolor{red}{Same modes were observed and analized in tetrahedrites\cite{May2016,Lai2015} with energies approximately 4, 9 and 18 meV (33, 72, 145 cm\textsuperscript{-1}). 
+The enegries of tetragidrite linked to the trigonally-bonded Cu atoms: the lowest energy is linked to Cu2 (they do not divide to Cu2 and Cu21), the middle --- to Cu1 and the highest --- to Sb.
+That in good agreement with our results.
+Thus, the reasons for the strong anharmonic behavior, described in the papers, is a dynamic disorder of the copper atoms and arsenic atoms.}
 Consequently, this leads to out-of-plane low frequency rattling modes, and a low lattice thermal conductivity.
@@
 \section{Conclusions}\label{sec:level1}
-In conclusion, the structural variety of synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13},  leads to  a dynamic disorder of the copper atoms, asymmetric bonds, and inconsistent electronic densities.
+In conclusion, the structural variety of synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13},  leads to  a dynamic disorder of the copper atoms, asymmetric bonds, and \textcolor{red}{different charge distribution}.
 This brings to the out-of-plane low frequency rattling modes, well described by Einstein characteristic temperatures: 74, 104, 115, and 185~K.

### 2021-01-26 paper_tennantite.tex

@@
 The thermal expansion of the crystal, and the corresponding change of the atomic vibration frequencies depend on the temperature, and may be described using a quasi-harmonic approximation\cite{willis1975thermal,Bentien2005}.
-As a result ADP, is described by u\textsubscript{calc}=xu\textsubscript{E}+(1-x)u\textsubscript{D}+u\textsubscript{static}, where xu\textsubscript{E} and (1-x)u\textsubscript{D} are Einstein and Debye parts, u\textsubscript{static} is a static shift of an atom from its site in the structure model\cite{Dudka2019}.
+As a result ADP, is described by u\textsubscript{calc}~$=$~xu\textsubscript{E}+(1-x)u\textsubscript{D}+u\textsubscript{static}, where xu\textsubscript{E} and (1-x)u\textsubscript{D} are Einstein and Debye parts, u\textsubscript{static} is a static shift of an atom from its site in the structure model\cite{Dudka2019}.
 The result of tennantite ADPs fitting is presented in the Fig.~\ref{fig:enst_temp}, and Table~\ref{tab:enst_temp}.
@@
 The maximal oscillation frequency of the selected atom and its characteristic Debye temperature, T\textsubscript{D}, corresponds to the case x~$=$~0.
-Distributions of zero-point oscillations, u\textsubscript{$0E$} or u\textsubscript{$0D$}, were obtained applying T~$=$~0 in the Einstein or Debye formulas.
-Thus, the contribution of Einstein or Debye parts to atomic displacements consists of zero quantum vibrations, u\textsubscript{$0E$} or u\textsubscript{$0D$}, and a temperature-dependent part, u\textsubscript{E}(T) or u\textsubscript{D}(T), which can be associated with the thermal motion of atoms.
-That is, u\textsubscript{E} = u\textsubscript{$0E$} + u\textsubscript{E}(T), and u\textsubscript{D} = u\textsubscript{$0D$} + u\textsubscript{D}(T).
-The shift of an atom from its equilibrium position due to any reason other than thermal vibrations is the sum of zero vibrations and static shift: u\textsubscript{shift} = u\textsubscript{$0E$} + u\textsubscript{static} or u\textsubscript{shift} = u\textsubscript{$0D$} + u\textsubscript{static}\cite{Dudka2019}.
+Distributions of zero-point oscillations, u\textsubscript{0E} or u\textsubscript{0D}, were obtained applying T~$=$~0 in the Einstein or Debye formulas.
+Thus, the contribution of Einstein or Debye parts to atomic displacements consists of zero quantum vibrations, u\textsubscript{0E} or u\textsubscript{0D}, and a temperature-dependent part, u\textsubscript{E}(T) or u\textsubscript{D}(T), which can be associated with the thermal motion of atoms.
+That is, u\textsubscript{E} = u\textsubscript{0E} + u\textsubscript{E}(T), and u\textsubscript{D} = u\textsubscript{0D} + u\textsubscript{D}(T).
+The shift of an atom from its equilibrium position due to any reason other than thermal vibrations is the sum of zero vibrations and static shift: u\textsubscript{shift} = u\textsubscript{0E} + u\textsubscript{static} or u\textsubscript{shift} = u\textsubscript{0D} + u\textsubscript{static}\cite{Dudka2019}.
 
@@
 \includegraphics[width=0.48\textwidth]{ADP_aproximation_eng}% Here is how to import EPS art
-\caption{\label{fig:enst_temp} Equivalent parameters U\textsubscript{eq} of the mean-square displacements of atoms in tennantite.
+\caption{\label{fig:enst_temp} Equivalent parameters u\textsubscript{eq} of the mean-square displacements of atoms in tennantite.
 Points are the experimental data.
@@
 \caption{\label{tab:enst_temp}
-Einstein temperatures, dispersions of zero-point oscillations u\textsubscript{$E_{0}$} u\textsubscript{static}, and u\textsubscript{shift} for atoms in tennantite.
+Einstein temperatures, dispersions of zero-point oscillations u\textsubscript{E$_{0}$} u\textsubscript{static}, and u\textsubscript{shift} for atoms in tennantite.
 $R=\sum |u\textsubscript{eq} - u\textsubscript{calc} |/\sum u\textsubscript{eq}$ is the residual factor of the LS procedure.

### 2021-01-30 paper_tennantite.tex

@@
 \textcolor{red}{The tennantite structure treated as sphalerite-type and belongs to \hmn{I -4 3 m} space group\cite{yaroslavzev2019,Makovicky_2006}.
-There are three copper position: Cu1 is tetrahedrally coordinated by four sulpfur atoms, Cu2 is coordinated by three sulpfur atoms and Cu21 is tetrahedrally coordinated by three sulpfur and arsenic atoms.
-The one arsenic is coordinated by three sulpfur atoms.
-Cu21 and Cu2 atoms possess very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view} right).}
+The structure can be described by five nonequivalent crystallographic sites: two for Cu, one for As, and two for S.
+Cu1 is tetrahedrally coordinated (CuS\textsubscript{4}) by four S1, Cu2 is trigonally coordinated (CuS\textsubscript{3}) by two S1 and one S2.
+As forms a trigonal pyramid (AsS\textsubscript{3}) with three S1.
+Additionally, the S2 is centered in an octahedral unit that is named the Laves polyhedra (SCu\textsubscript{6}) with six copper atoms in sites Cu2 and Cu21.
+Cu21 and Cu2 atoms possess very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view} right).
+}
 In a case of tennantite- and tetrahedrite-based materials, it is generally considered, that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen \textcolor{red}{{\it p}} orbitals\cite{Lai2015}.
@@
 
-Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) indicate the potential instability of this position. 
-\textcolor{red}{According to structurel study of tennantie Cu2\cite{Hathwar2019} position may be describied as 6 differnt Cu position.
-But according our study even after dividing Cu2 position into Cu2 and Cu 21, the Cu2 position remains highly disordered and there are no reasons for adding additional positions.}
+Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) \textcolor{red}{approved instability of this site\cite{Hathwar2019,yaroslavzev2019}}.
 This disordering is reliably described by the anharmonic model of atomic displacements using the Gram-Charlier expansion to the 4th order.
@@
 \textcolor{red}{Same modes were observed and analized in tetrahedrites\cite{May2016,Lai2015} with energies approximately 4, 9 and 18 meV (33, 72, 145 cm\textsuperscript{-1}).
-The enegries of tetragidrite linked to the trigonally-bonded Cu atoms: the lowest energy is linked to Cu2 (they do not divide to Cu2 and Cu21), the middle --- to Cu1 and the highest --- to Sb.
 That in good agreement with our results.
-Thus, the reasons for the strong anharmonic behavior, described in the papers, is a dynamic disorder of the copper atoms and arsenic atoms.}
+Thus, the reasons for the strong anharmonic behavior is a dynamic disorder of the copper atoms and arsenic atoms.}
 Consequently, this leads to out-of-plane low frequency rattling modes, and a low lattice thermal conductivity.

### 2021-01-30 paper_tennantite.tex

@@
 The structure can be described by five nonequivalent crystallographic sites: two for Cu, one for As, and two for S.
-Cu1 is tetrahedrally coordinated (CuS\textsubscript{4}) by four S1, Cu2 is trigonally coordinated (CuS\textsubscript{3}) by two S1 and one S2.
-As forms a trigonal pyramid (AsS\textsubscript{3}) with three S1.
+Cu1 is tetrahedrally coordinated (CuS\textsubscript{4}) by four S1 and As forms a trigonal pyramid (AsS\textsubscript{3}) with three S1.
 Additionally, the S2 is centered in an octahedral unit that is named the Laves polyhedra (SCu\textsubscript{6}) with six copper atoms in sites Cu2 and Cu21.
+Cu2 is trigonally coordinated (CuS\textsubscript{3}) by two S1 and one S2, Cu21 is coordinated by two S1, one S2 and one As.
 Cu21 and Cu2 atoms possess very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view} right).
@@
 We can also observe certain similarities between tennantite and inorganic compounds featuring atoms with  {\it 3d\textsuperscript{9}}  configuration, and having asymmetric Fermi surface.
-The resulting complex charge distribution, and variances in the copper atom states, may, in turn, be the reason for complex exchange interactions and the reported AFM ordering\cite{yaroslavzev2019} in tennantite.
+\textcolor{red}{The resulting complex charge distribution, and variances in the copper atom charges and, therefore, effective oxidation states, caused by structural shifts, may, in turn, be the reason for complex exchange interactions and the reported AFM ordering\cite{yaroslavzev2019} in tennantite.}
 Moreover, the same structure features have been described for tetrahedrite\cite{DiPaola2020}.

### 2021-02-02 paper_tennantite.tex
proofreading

@@
 \documentclass[preprint,review,12pt]{elsarticle}
+\biboptions{sort&compress}
 
@@
 \author[MSU]{Andrei~V.~Mironov}
-\author[MIPT,TISNCM]{Sergey~G.~Buga}
+\author[TISNCM]{Sergey~G.~Buga}
 \author[TISNCM]{Vladimir~V.~Denisov}
@@
 \address[SIC]{Shubnikov Institute of Crystallography of Federal Scientific Research Centre “Crystallography and Photonics” of Russian Academy of Sciences, Leninskiy Prospekt 59, 119333, Moscow, Russia}
-\address[MIPT]{Moscow Institute of Physics and Technology, 141700, 9 Institutsky lane, Dolgoprudny, Russia}
 
@@
 Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedri\textcolor{red}{t}e group with a low lattice thermal conductivity.
-\textcolor{red}{Combined data from high-quality X-ray diffraction, electron microscopy (STEM--HAADF), Raman spectroscopy, as well as DFT calculations are used to analyze the peculiarities of structure stability and dynamics.
-A atomic displacement parameters and low-energy optical phonon modes are discussed within the context of the structure variations and pecularities of the charge distributions.
-The latter indicates that the tennantite structure tends to conform to the covalent polar bonds and its charge distribution significantly affected by the atomic shifts in Laves polyhedra.
-According to the DFT calculations, there is a population of stable model structures with varying shifts of copper atoms in Laves polyhedra, with total energies being very close (within 0.24~eV), which can explain the observed behavior of the atomic displacement parameters.}
-A specially designed  technique used for the experimental analysis of the atomic displacement parameters  revealed Einstein characteristic temperatures in the tennantite structure to be in the range of 50--190~K, attributed to  low-energy optical phonon modes.
+\textcolor{red}{Combined data from high-quality X-ray diffraction, electron microscopy (STEM--HAADF), Raman spectroscopy, as well as DFT calculations are used to analyze the peculiarities of its structure stability and dynamics.
+Atomic displacement parameters (ADP) and low-energy optical phonon modes are discussed within the context of the structure variations and pecularities of the charge distribution.
+The latter indicates that the tennantite structure tends to conform to the covalent polar bonds and its charge distribution is significantly affected by the atomic shifts in Laves polyhedra.
+According to the DFT calculations, there is a population of stable model structures with varying shifts of copper atoms in Laves polyhedra, with total energies being very close (within 0.24~eV), which can explain the observed behavior of the ADP.
+A specially designed  technique is used for the experimental analysis of the ADP that revealed Einstein characteristic temperatures in the tennantite structure to be in the range of 50--190~K, which is attributed to  low-energy optical phonon modes.}
 
@@
   \item DFT calculations reveal a mixed valence of Cu atoms, and Laves \textcolor{red}{polyhedra} distortions
-  \item Jahn-Teller distortions give rise to a set of unit cells with close ground energies
+  \item Jahn-Teller distortions give rise to a set of unit cells with close \textcolor{red}{ground} state energies
   \item Rattling vibration modes refer to Einstein temperatures of 74, 104, 115, 185K
@@
 thermoelectic materials\sep
-DFT\sep
-anisotropy\sep
-optical spectroscopy\sep
+DFT calculations\sep
+structural anisotropy\sep
+Raman spectroscopy\sep
 X-ray diffraction\sep
@@
 
-The tennantite-tetrahedri\textcolor{red}{t}e group represents a large class of inorganic compounds including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
-Despite being known for over two centuries, these minerals are still under investigation, both due to  structural peculiarities and potential applications.
-Arsenic- and antimony-containing compounds of this class are the advanced thermoelectric materials with a low lattice thermal conductivity\cite{Sootsman2009,Chetty2015}.
-\textcolor{red}{For example, the studies of tetrahedrite doped with Mn, Fe, Co, Ni, Zn, Te, Se showed ZT values in the range from 0.2 to 1.13\cite{Heo2014,Suekuni2013,Lu2012,Barbier2016,Rout2020,Zhu2019}.}
+The tennantite-tetrahedri\textcolor{red}{t}e group represents a large class of inorganic compounds, including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
+Despite being known for over two centuries, these minerals still represent objects of intense studies, both due to  structural peculiarities and potential applications.
+Arsenic- and antimony-containing compounds of this class are considered as advanced thermoelectric materials with a low lattice thermal conductivity\cite{Sootsman2009,Chetty2015}.
+\textcolor{red}{For instance, tetrahedrite doped with Mn, Fe, Co, Ni, Zn, Te, Se showed ZT values in the range from 0.2 to 1.13\cite{Heo2014,Suekuni2013,Lu2012,Barbier2016,Rout2020,Zhu2019}.}
 
-\textcolor{red}{The tennantite structure treated as sphalerite-type and belongs to \hmn{I -4 3 m} space group\cite{yaroslavzev2019,Makovicky_2006}.
+\textcolor{red}{The tennantite structure is treated as a sphalerite-type, thus conforms to the \hmn{I -4 3 m} space group\cite{yaroslavzev2019,Makovicky_2006}.
 The structure can be described by five nonequivalent crystallographic sites: two for Cu, one for As, and two for S.
-Cu1 is tetrahedrally coordinated (CuS\textsubscript{4}) by four S1 and As forms a trigonal pyramid (AsS\textsubscript{3}) with three S1.
-Additionally, the S2 is centered in an octahedral unit that is named the Laves polyhedra (SCu\textsubscript{6}) with six copper atoms in sites Cu2 and Cu21.
-Cu2 is trigonally coordinated (CuS\textsubscript{3}) by two S1 and one S2, Cu21 is coordinated by two S1, one S2 and one As.
-Cu21 and Cu2 atoms possess very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view} right).
+Cu1 is tetrahedrally coordinated (CuS\textsubscript{4}) by four S1, and As forms a trigonal pyramid (AsS\textsubscript{3}) with three S1.
+Additionally, the S2 is a center of an octahedral unit that is called a Laves polyhedra (SCu\textsubscript{6}) with six copper atoms in sites Cu2 and Cu21.
+Cu2 is trigonally coordinated (CuS\textsubscript{3}) by two S1 and one S2, while Cu21 is coordinated by two S1, one S2 and one As atoms.
+Cu21 and Cu2 atoms show very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view}, right).
 }
-In a case of tennantite- and tetrahedrite-based materials, it is generally considered, that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen \textcolor{red}{{\it p}} orbitals\cite{Lai2015}.
+In a case of tennantite- and tetrahedrite-based materials, it is generally considered that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen \textcolor{red}{{\it p}} orbitals\cite{Lai2015}.
 Such a hybridization leads to a bonding asymmetry, and out-of-plane low frequency rattling modes, which are quasi-localized and anharmonic\cite{May2016,Bouyrie2015}.
@@
 \subfigure{\includegraphics[width=0.35\columnwidth]{general_view_laves}}
-\caption{\label{fig:generel_view} \textcolor{red}{Left --- the view of the Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} tennantite structure and of coordination polyhedra around the Cu1 (blue) and the Laves polyhedra (yellow); right --- the Laves polyhedra with Cu2 and Cu21 atoms with occupancy.} }
+\caption{\label{fig:generel_view} \textcolor{red}{Left --- the Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} tennantite structure with coordination polyhedra around the Cu1 (blue), and the Laves polyhedra (yellow); right --- the Laves polyhedra containing Cu2 and Cu21 atoms with their partial occupancies shown as sections of spheres.} }
 \end{figure}
@@
 
-Recently, we performed a multi-temperature (90--298~K) structural study of a synthetic tennantite\cite{yaroslavzev2019} and found that below ca.
-120 K the copper atom distribution in tennantite changes from a more statistically delocalized Cu2 a well-defined split into Cu2 and Cu21 positions without a first-order phase transition.
-This effect is accompanied by As1 and S2 atoms displacement, which was also observed in ref.~ \cite{Hathwar2019}.
+Recently, we have performed a multi-temperature (90--298~K) structural study of a synthetic tennantite\cite{yaroslavzev2019} and found that below ca.
+120 K the copper atom distribution in tennantite changes from a more statistically delocalized Cu2 to a well-defined split into Cu2 and Cu21 positions without a first-order phase transition.
+This effect is accompanied by As1 and S2 atoms displacement, which was also observed in \textcolor{red}{Ref.}~\cite{Hathwar2019}.
 We also investigated the low- and room-temperature electronic structures of a synthetic tennantite based on the DFT calculations, which confirmed the second-order transition from the low-temperature AFM to the room-temperature PM state\cite{yaroslavzev2019}.
 
-However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves \textcolor{red}{polyhedra} in the structure, were left aside in the previous paper\cite{yaroslavzev2019}.
-In this paper, we focus on these problems, and  investigate the tennantite cell energy distribution, and the charge density differences for different Cu positions in Laves polyhedra.
-Also, we consider low-energy phonon modes, and peculiarities of the atomic displacement parameters in the temperature range of 85--293~K, the same as in Ref.~\cite{Dudka2019}, in a context of the cell energy distribution.
-To clarify distortions in Laves polyhedra, a study of the spherical single-crystal sample was performed and the high-angle annular dark-field (HAADF) image was obtained.
+However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves \textcolor{red}{polyhedra} in the structure, were put aside in the previous paper\cite{yaroslavzev2019}.
+In this paper, we focus on these problems, and  investigate the tennantite cell energy distribution, and the charge density differences for different Cu positions in the Laves polyhedra.
+Also, we investigate low-energy phonon modes, and peculiarities of the ADP in the temperature range of 85--293~K, the same as in Ref.~\cite{Dudka2019}, in the context of the cell energy distribution.
+To clarify the distortions in Laves polyhedra, a study of the spherical single-crystal sample was performed and the high-angle annular dark-field (HAADF) images were obtained.
 
@@
 High quality single crystals of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} for the XRD analysis were grown using a two-step procedure.
-At first, bulk Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} has been prepared by a high-temperature technique from copper (99.5~\%), arsenic (99.5~\%), and sulpher (99.5~\%).
+At first, bulk Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} has been prepared by a high-temperature technique from copper (99.5~\%), arsenic (99.5~\%), and sulphur (99.5~\%).
 Then, the ingots were subjected to directional recrystallization by the Bridgman-Stockbarger technique in a two-zone furnace.
 The temperature in the recrystallization zone was chosen 40 K~above the tennantite melting point.
-A speed of the  ingot motion was 0.5~mm/hour, with the temperature gradient in the recrystallization zone about 8--10~K/mm.
+A speed of the ingot motion was set at 0.5~mm/hour, with the temperature gradient in the recrystallization zone ca.~8--10~K/mm.
 
 \subsection{Single-crystal X-ray diffraction}\label{sec:level2}
-A spherical shape single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study\cite{Becker1975}.
-Enraf-Nonius CAD-4 diffractometer with AgK\textsubscript{$\alpha$} and graphite monochromator was used.
-The spherical shape single-crystal structural study results are presented in Appendix, they are compared with the structural data \textcolor{red}{from} the \textcolor{red}{polyhedra} defined form sample\cite{yaroslavzev2019}.
+A spherically shaped single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study\cite{Becker1975}.
+Enraf-Nonius CAD-4 diffractometer with AgK\textsubscript{$\alpha$} equipped with graphite monochromator was used for the data collection.
+The spherical single-crystal structural study results are presented in Supplementary Material, and they are compared with the structural data \textcolor{red}{from} the \textcolor{red}{regularly shaped crystal} sample\cite{yaroslavzev2019}.
 
@@
 The sample has a rectangular shape with the dimensions of 0.456~$\times$~0.31~$\times$~0.247~mm\textsuperscript{3}.
-Xcalibur diffractometer equipped with a CCD EOS S2 detector (Rigaku Oxford Diffraction), MoK\textsubscript{$\alpha$} and Cobra Plus (Oxford Cryosystems) with nitrogen gas flow were used.
-The original experimental methods and data processing are presented in Appendix in details.
+Xcalibur diffractometer equipped with a CCD EOS S2 detector (Rigaku Oxford Diffraction, MoK\textsubscript{$\alpha$}) and Cobra Plus (Oxford Cryosystems) apparatus with nitrogen gas flow combination were used for the data collection.
+The original experimental methods and data processing are presented in Supplementary Material in details.
 
 \subsection{Theoretical calculations}\label{sec:level2}
-Calculations of the stability of possible tennantite polytypes were performed based on Density Function Theory (DFT)\cite{Kohn1965} within the generalized gradient approximation (GGA) using Perdew-Burke-Ernzerhof exchange-correlation functional\cite{Perdew1996}.
+Calculations on the stability of possible tennantite polytypes were performed based on Density Function Theory (DFT)\cite{Kohn1965} within the generalized gradient approximation (GGA) using Perdew-Burke-Ernzerhof exchange-correlation functional\cite{Perdew1996}.
 We used the projector augmented wave method\cite{Blchl1994} with the periodic boundary conditions as implemented in Vienna Ab-initio Simulation Package (VASP)\cite{Kresse1996,Kresse1996-2,Kresse1993,Kresse1994}.
 The plane-wave energy cut-off was set to 450~eV.
-To calculate the equilibrium atomic structure, the Brillouin zone was sampled according to the Monkhorst–Pack scheme\cite{Monkhorst1976} with a 6$\times$6$\times$6 grid in the k-space.
+To calculate the equilibrium atomic structure, the Brillouin zone was sampled according to the Monkhorst–Pack scheme\cite{Monkhorst1976} with a 6$\times$6$\times$6 grid in the {\it k}-space.
 The convergence criterion for the structural relaxation was set at 0.1~meV.
@@
 \subsection{Electron microscopy}\label{sec:level2}
-High-resolution electron microscopy images were taken using FEI~Titan~80--300 transmission electron microscope in the HAADF--STEM mode (scanning translucent) with an acceleration voltage of 300~kV.
+High-resolution electron microscopy images were taken using FEI~Titan~80--300 transmission electron microscope in the HAADF--STEM mode (high-angle annular dark-field scanning transmission) with an acceleration voltage of 300~kV.
 The sample for microscopy was prepared using FEI~Helios~600 focused ion beam setup.
-HAADF image was fitted by Atomap\cite{Nord2017} package in Python.
+HAADF image was fitted by Atomap\cite{Nord2017} package written in Python.
 
@@
 Calibration was performed using 520.5~cm\textsuperscript{-1} Raman peak of a polished silicon wafer. 
-For observation of lines near the laser line we used 3~ONDAX~114-ER297-001 fiber Bragg gratings.
-Fittings of the Raman spectra were performed by the LMFIT\cite{LMFIT} package in Python.
+We used 3~ONDAX~114-ER297-001 fiber Bragg gratings to observe lines near the laser one.
+Fittings of the Raman spectra were performed by the LMFIT\cite{LMFIT} package written in Python.
 The fitting model was based on 6 pseudo-Voigt functions and a polynomial function for the background.
@@
 \subsection{Remarks on the structure of synthetic tennantite}\label{sec:level2}
-Study of the high-grade single crystal allowed us to re-investigate the crystal structure of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  with a high precision.
-\textcolor{red}{The structure was refined in a way similar to described early\cite{yaroslavzev2019}.
+The study of the high quality single crystal allowed us to re-investigate the crystal structure of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  with a high precision.
+\textcolor{red}{The structure was refined in a way similar to previously described in Ref.~\cite{yaroslavzev2019}.
 The sum of occupancies for Cu2, Cu21 and its symmetry related site were constrained to 1.
@@
 The maximum entropy method (MEM) refinement gave the result identical to \cite{yaroslavzev2019}.}
-Our data confirms that the compound contains 12 copper atoms per formula unit, and shows no evidences of a copper deficiency.
+Our data confirms that the compound contains 12 copper atoms per formula unit, and shows no evidence of copper deficiency.
 Neither XRD, nor TEM data \textcolor{red}{have shown detectable packing defects}.
@@
 
-Due to the crystal growth method used, anisotropic extinction in the sample takes place. Extinction parameters are presented in the Table~\ref{tab:anis_ext}.
+Due to the crystal growth method used, the sample shows a degree of anisotropic extinction. Extinction parameters are presented in the Table~\ref{tab:anis_ext}.
 \textcolor{red}{The disorder of Cu21} is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
-The electron diffraction, and overlay of HAADF image with the tennantite crystal [110] zone generated by VESTA\cite{Momma2011}, are shown in Appendix.
-The processed HAADF image (Fig.~\ref{fig:micro} right) shows  the ellipticity for the Cu/As atomic columns, which is a measure of the atomic column elongation\cite{Nord2017}.
-The atomic column elongation is explained by the blurring of the intensity distribution, and a large atomic displacement.
-A similar inhomogeneous electron density was observed in tetrahedrite\cite{Mishra2017}, and tetrahedral framework structure\cite{Suekuni2019}.
-Also, the anisotropy may be caused by the crystal growth conditions or/and a crystal cell distortion.
-If so, then the structure would have a diagonal distortion or/and have more or less than 12 copper atoms per cell, which is not the case.
+The electron diffraction, and overlay of HAADF image with the tennantite crystal [110] zone generated by VESTA\cite{Momma2011}, are given in Supplementary Material.
+Processed HAADF image (Fig.~\ref{fig:micro}, right) shows  an ellipticity for the Cu/As atomic columns, which is a measure of the atomic column elongation\cite{Nord2017}.
+The atomic column elongation is evidenced by the blurring of the intensity distribution, and a large atomic displacement.
+Similar effects were observed in tetrahedrite\cite{Mishra2017}, and several tetrahedral framework structures\cite{Suekuni2019}.
+Also, the observed anisotropic displacement may possibly be caused by the crystal growth conditions or/and a crystal cell distortion.
+However, in such case the structure must show prominent diagonal distortion and/or feature an increase or decrease of the copper content per cell (with respect to 12 copper atoms), which is not the case.
 
@@
 
-\subsection{Atomic displacement parameters analysis of the temperature dynamics based on diffraction data}\label{sec:level2}
+\subsection{Atomic displacement parameter temperature dynamics analysis based on diffraction data}\label{sec:level2}
 
-The atomic displacement parameters (ADPs) were analyzed by DebyeFit program using the structural data.
-The DebyeFit estimates the Debye or/and Einstein characteristic temperature in crystals from the equivalent atomic displacement parameters obtained at different temperatures.
+The ADP were analyzed by DebyeFit program using the crystallographic data.
+The DebyeFit estimates the Debye or/and Einstein characteristic temperature in crystals from the equivalent ADP obtained at different temperatures.
 
@@
 The thermal expansion of the crystal, and the corresponding change of the atomic vibration frequencies depend on the temperature, and may be described using a quasi-harmonic approximation\cite{willis1975thermal,Bentien2005}.
-As a result ADP, is described by u\textsubscript{calc}~$=$~xu\textsubscript{E}+(1-x)u\textsubscript{D}+u\textsubscript{static}, where xu\textsubscript{E} and (1-x)u\textsubscript{D} are Einstein and Debye parts, u\textsubscript{static} is a static shift of an atom from its site in the structure model\cite{Dudka2019}.
-The result of tennantite ADPs fitting is presented in the Fig.~\ref{fig:enst_temp}, and Table~\ref{tab:enst_temp}.
+As a result, ADP is described by u\textsubscript{calc}~$=$~xu\textsubscript{E}+(1-x)u\textsubscript{D}+u\textsubscript{static}, where xu\textsubscript{E} and (1-x)u\textsubscript{D} are Einstein and Debye parts, u\textsubscript{static} is a static shift of an atom from its site in the structure model\cite{Dudka2019}.
+The result of tennantite ADP fitting is presented in the Fig.~\ref{fig:enst_temp}, and Table~\ref{tab:enst_temp}.
 The average oscillation frequency of the selected atom, and its characteristic Einstein temperature, T\textsubscript{E}, can be obtained  assuming x~$=$~1.
@@
 Points are the experimental data.
-The solid curves show the fit of the temperature dependences according to the expanded Einstein model.}
+Solid curves show the fit of the temperature dependences according to the expanded Einstein model.}
 \end{figure}
 
-Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) \textcolor{red}{approved instability of this site\cite{Hathwar2019,yaroslavzev2019}}.
-This disordering is reliably described by the anharmonic model of atomic displacements using the Gram-Charlier expansion to the 4th order.
+Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) \textcolor{red}{confirmed instability of this site\cite{Hathwar2019,yaroslavzev2019}}.
+This disorder is reliably described by the anharmonic model of atomic displacements using the Gram-Charlier expansion to the 4th order.
 
@@
 
-Within \textcolor{red}{approach above}, the Einstein solid model is used to describe independent harmonic oscillators.
-If so, the low energy spectrum should consist of peaks with the Einstein's energies, which we found by DebyeFit (Table~\ref{tab:enst_temp}).
-Results of calculations are presented in Figure~\ref{fig:low_energ_raman}.
-The Einstein's energies from structural study were used as the initial points for the fit, and in Table~\ref{tab:ram_fit} the initial  and fitted wavenumbers are presented.
+Within \textcolor{red}{the approach above}, the Einstein solid model is used to describe independent harmonic oscillators.
+Thus, the low energy spectrum should consist of peaks with the Einstein's energies, which we found by DebyeFit (Table~\ref{tab:enst_temp}).
+The results of the calculations are presented in Figure~\ref{fig:low_energ_raman}.
+The Einstein's energies from structural study were used as the initial points for the fit, with the initial and fitted wavenumbers are presented and in Table~\ref{tab:ram_fit}.
 The low energy $l_{1}$ and $l_{2}$ peaks are well described by Einstein's energies of Cu2, Cu21, Cu1, and As (66, 40, 79, and 122 cm\textsuperscript{-1} respectively).
-\textcolor{red}{Same modes were observed and analized in tetrahedrites\cite{May2016,Lai2015} with energies approximately 4, 9 and 18 meV (33, 72, 145 cm\textsuperscript{-1}).
-That in good agreement with our results.
-Thus, the reasons for the strong anharmonic behavior is a dynamic disorder of the copper atoms and arsenic atoms.}
+\textcolor{red}{Same modes were observed and analyzed in tetrahedrites\cite{May2016,Lai2015} with energies approximately 4, 9 and 18 meV (33, 72, 145 cm\textsuperscript{-1}) which is
+in good agreement with our results.
+Thus, we can state that the reason for the strong anharmonic behavior is a dynamic disorder of the copper atoms and arsenic atoms.}
 Consequently, this leads to out-of-plane low frequency rattling modes, and a low lattice thermal conductivity.
@@
 \includegraphics[width=0.48\textwidth]{raman_25_CuAsS3_low_energy}
-\caption{\label{fig:low_energ_raman} The Raman spectrum of the tennantite crystal  below 200 cm\textsuperscript{-1}.
+\caption{\label{fig:low_energ_raman} Raman spectrum of the tennantite crystal  below 200 cm\textsuperscript{-1}.
 Experimental peaks are considered as the peaks with Einstein's energies.
@@
 As an initial point, we considered tennantite structure described in  \hmn{I -4 2 m}\ space group (henceforth called {\it reference structure}).
-The unit cell contains Laves \textcolor{red}{polyhedra} formed by copper atoms around sulpher ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
+The unit cell contains Laves \textcolor{red}{polyhedra} formed by copper atoms around sulphur ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
 By shifting copper atoms by ca.
@@
 \textcolor{red}{In the DFT calculations, where we cannot have Cu2 and Cu21 at the same time since we cannot have part of an atom occupying a position within a single polyhedron, we prefer to only use Cu2 notation, but distinguish their positions before and after optimization.}
-The Laves \textcolor{red}{polyhedra} morphologies before, and after the optimization, are shown in Figure~\ref{fig:init_and_opt_laves}.
-The total energy differences between the initial tennantite and optimized structures are shown in Figure~\ref{fig:energy_structure_rescale}.
+The Laves \textcolor{red}{polyhedra} morphologies before and after the optimization are shown in Figure~\ref{fig:init_and_opt_laves}.
+Total energy differences between the reference structure of initial tennantite and optimized structures are shown in Figure~\ref{fig:energy_structure_rescale}.
 
@@
  \includegraphics[width=0.48\textwidth]{Init_and_opt_renamed}
- \caption{\label{fig:init_and_opt_laves} Geometries of SCu\textsubscript{6} Laves \textcolor{red}{polyhedra} before, and after structural optimization.
-Sulpher atoms are shown in yellow, copper atoms before optimization are shown in grey, and after optimization in blue.
-VESTA\cite{Momma2011} was used for visualisation.
+ \caption{\label{fig:init_and_opt_laves} The geometries of SCu\textsubscript{6} Laves \textcolor{red}{polyhedra} before and after structural optimization.
+sulphur atoms are shown in yellow, copper atoms before optimization are shown in grey, and after optimization in blue.
+VESTA\cite{Momma2011} was used for the visualisation.
 }
@@
 
-Our calculations show, that the experimentally determined synthetic tennantite structure is not the most energy favorable one at 0~K.
+Our calculations indicate that the experimentally determined synthetic tennantite structure is not the most energy favorable one at 0~K.
 
-We observe 8 structures in our population with the energies less than the starting one.
-They correspond to the structures No's 2, 3, 9, 11, 14, 17, 18, and 19, with the last one  possessing the the lowest energy.
-The coordination of the central sulpher atom deviates quite a lot from an ideal octahedral, with the energy gain being achieved by shifting one (structure 9), two (structures 17, 18), or three (structures 2, 3, 11, 14, 19) atoms.
+We observe 8 structures in our population with the energies less than the reference one.
+They correspond to the structures No's 2, 3, 9, 11, 14, 17, 18, and 19, with the last one  possessing the lowest energy.
+The coordination of the central sulphur atom deviates quite a lot from an ideal octahedron, with the energy gain being achieved by shifting one (structure 9), two (structures 17, 18), or three (structures 2, 3, 11, 14, 19) atoms.
 
@@
 $+1$ and $+2$).
-Charge density on arsenic affects substantially the respective charge density at 1st sulpher position (see~Appendix), and has a minor effect on Cu2 charges, while Cu1 is virtually unaffected by any change.
-The other sulpher atom shows minor charge fluctuations, and they appear to be not directly associated with the state of arsenic.
+Charge density on arsenic affects substantially the respective charge density at 1st sulphur position (see~Supplementary Material), and has a minor effect on Cu2 charges, while Cu1 is virtually unaffected by any change.
+The other sulphur atom shows minor charge fluctuations, and they appear to be not directly associated with the oxidation state of arsenic.
 
@@
 It must be noted that the majority of the favorable structures belongs to group 2, i.e.
-more covalent structures with both arsenic and sulpher atoms showing the relatively low positive and negative charges, respectively.
+more covalent structures with both arsenic and sulphur atoms showing relatively low positive and negative charges, respectively.
 Interestingly, the reference structure is significantly more ionic in this respect.
@@
 \section{Conclusions}\label{sec:level1}
-In conclusion, the structural variety of synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13},  leads to  a dynamic disorder of the copper atoms, asymmetric bonds, and \textcolor{red}{different charge distribution}.
-This brings to the out-of-plane low frequency rattling modes, well described by Einstein characteristic temperatures: 74, 104, 115, and 185~K.
-The peculiarities of the tennantite crystal and electronic structures lead to asymmetric Fermi surface, thus makinkg tennantite--tetrahedrite group compounds attractive research objects.
+In conclusion, using a combination of several experimental techniques, we have investigated the structural variations of synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, manifesting itself as a dynamic disorder of the copper atoms.
+\textcolor{red}{The tennantite structure tends to conform to the asymmetric covalent polar bonds and its charge distribution is significantly affected by the atomic shifts in Laves polyhedra.
+These effects, in turn, give rise to the out-of-plane low frequency rattling modes, well described by Einstein characteristic temperatures: 74, 104, 115, and 185~K.
+The peculiarities of the tennantite crystal and electronic structure, including lattice dynamics and shifting charge distribution, shows similarities between this compound and inorganic compounds with an asymmetric Fermi surface, thus making tennantite--tetrahedrite group attractive research objects.}
 
-Our extensive structural studies revealed a strong electron density anisotropy of the bulk sample, with no evidence of a distortion or local defects.
+Our extensive structural studies revealed a strong tendency of anisotropic shifts in electron density of the bulk sample, with no evidence of a distortion or local defects.
 
-The specially-designed  technique was tested for the experimental ADPs analysis, and we have demonstrated a new method of the experimental study of a crystal structure.
+The specially-designed technique was successfully tested for the experimental ADP analysis, and, as we have demonstrated, can be used as a new method of the experimental study of a crystal structure.
 
@@
 National Research Center “Kurchatov Institute“.
-We thank I. A. Perezhogin for valuable comments and  Professor A. N. Babushkin for the tennantit ingot.
+We thank I. A. Perezhogin for valuable comments and  Professor A. N. Babushkin for the tennantite ingot.
 

### 2021-02-03 SM/paper_tennantite.tex
proofreading
non highlighted text

@@
 The calculation of integral intensities from diffraction patterns was performed using the CrysAlisPro program\cite{Rigaku}.
-The data processing included: consideration of geometric features of the data collection (Lorentz correction) and correction for polarization of radiation; calibration of the diffractometer\cite{Dudka2010}; absorption correction for \textcolor{red}{polyhedra} samples (performed by the Gaussian integration method\cite{Busing1957}); refinement of the half-wavelength contribution\cite{Dudka2010_2}; the correction for an extinction\cite{Becker1974}.
+The data processing included: consideration of geometric features of the data collection (Lorentz correction) and correction for polarization of radiation; calibration of the diffractometer\cite{Dudka2010}; absorption correction for polyhedra samples (performed by the Gaussian integration method\cite{Busing1957}); refinement of the half-wavelength contribution\cite{Dudka2010_2}; the correction for an extinction\cite{Becker1974}.
 The corrections and refinement of structural parameters were performed in the Jana2006\cite{Petek2014} and ASTRA programs\cite{Dudka2007}.

### 2021-02-03 paper_tennantite0.tex
non highlighted text

--- 2021-02-02 paper_tennantite.tex
@@
 \begin{abstract}
-Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedri\textcolor{red}{t}e group with a low lattice thermal conductivity.
-\textcolor{red}{Combined data from high-quality X-ray diffraction, electron microscopy (STEM--HAADF), Raman spectroscopy, as well as DFT calculations are used to analyze the peculiarities of its structure stability and dynamics.
+Synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, is the analogue of an abundant mineral that belongs to the tennantite-tetrahedrite group with a low lattice thermal conductivity.
+Combined data from high-quality X-ray diffraction, electron microscopy (STEM--HAADF), Raman spectroscopy, as well as DFT calculations are used to analyze the peculiarities of its structure stability and dynamics.
 Atomic displacement parameters (ADP) and low-energy optical phonon modes are discussed within the context of the structure variations and pecularities of the charge distribution.
@@
 According to the DFT calculations, there is a population of stable model structures with varying shifts of copper atoms in Laves polyhedra, with total energies being very close (within 0.24~eV), which can explain the observed behavior of the ADP.
-A specially designed  technique is used for the experimental analysis of the ADP that revealed Einstein characteristic temperatures in the tennantite structure to be in the range of 50--190~K, which is attributed to  low-energy optical phonon modes.}
+A specially designed  technique is used for the experimental analysis of the ADP that revealed Einstein characteristic temperatures in the tennantite structure to be in the range of 50--190~K, which is attributed to  low-energy optical phonon modes.
 
@@
 \begin{itemize}
-  \item Synthetic tennantite Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} structure consists of disordered Laves \textcolor{red}{polyhedra}
-  \item DFT calculations reveal a mixed valence of Cu atoms, and Laves \textcolor{red}{polyhedra} distortions
-  \item Jahn-Teller distortions give rise to a set of unit cells with close \textcolor{red}{ground} state energies
+  \item Synthetic tennantite Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} structure consists of disordered Laves polyhedra
+  \item DFT calculations reveal a mixed valence of Cu atoms, and Laves polyhedra distortions
+  \item Jahn-Teller distortions give rise to a set of unit cells with close ground state energies
   \item Rattling vibration modes refer to Einstein temperatures of 74, 104, 115, 185K
@@
 
-The tennantite-tetrahedri\textcolor{red}{t}e group represents a large class of inorganic compounds, including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
+The tennantite-tetrahedrite group represents a large class of inorganic compounds, including complex copper sulfosalts with the general formula Cu\textsubscript{10+x}M\textsubscript{2-x}X\textsubscript{4}S\textsubscript{13}, where M is a transition metal (Zn, Fe, Hg, etc.), and X is a pnictogen (As, Sb, or Bi) \cite{Makovicky_2006}, with the pure tennantite itself represented by the formula Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.
 Despite being known for over two centuries, these minerals still represent objects of intense studies, both due to  structural peculiarities and potential applications.
 Arsenic- and antimony-containing compounds of this class are considered as advanced thermoelectric materials with a low lattice thermal conductivity\cite{Sootsman2009,Chetty2015}.
-\textcolor{red}{For instance, tetrahedrite doped with Mn, Fe, Co, Ni, Zn, Te, Se showed ZT values in the range from 0.2 to 1.13\cite{Heo2014,Suekuni2013,Lu2012,Barbier2016,Rout2020,Zhu2019}.}
+For instance, tetrahedrite doped with Mn, Fe, Co, Ni, Zn, Te, Se showed ZT values in the range from 0.2 to 1.13\cite{Heo2014,Suekuni2013,Lu2012,Barbier2016,Rout2020,Zhu2019}.
 
-\textcolor{red}{The tennantite structure is treated as a sphalerite-type, thus conforms to the \hmn{I -4 3 m} space group\cite{yaroslavzev2019,Makovicky_2006}.
+The tennantite structure is treated as a sphalerite-type, thus conforms to the \hmn{I -4 3 m} space group\cite{yaroslavzev2019,Makovicky_2006}.
 The structure can be described by five nonequivalent crystallographic sites: two for Cu, one for As, and two for S.
@@
 Cu21 and Cu2 atoms show very large atomic displacements perpendicular to the plane of the triangle (Fig.~\ref{fig:generel_view}, right).
-}
-In a case of tennantite- and tetrahedrite-based materials, it is generally considered that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen \textcolor{red}{{\it p}} orbitals\cite{Lai2015}.
+
+In a case of tennantite- and tetrahedrite-based materials, it is generally considered that a low lattice thermal conductivity is caused by hybridized Cu {\it 3d}  and chalcogen {\it p} orbitals\cite{Lai2015}.
 Such a hybridization leads to a bonding asymmetry, and out-of-plane low frequency rattling modes, which are quasi-localized and anharmonic\cite{May2016,Bouyrie2015}.
@@
 \subfigure{\includegraphics[width=0.35\columnwidth]{general_view_laves}}
-\caption{\label{fig:generel_view} \textcolor{red}{Left --- the Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} tennantite structure with coordination polyhedra around the Cu1 (blue), and the Laves polyhedra (yellow); right --- the Laves polyhedra containing Cu2 and Cu21 atoms with their partial occupancies shown as sections of spheres.} }
+\caption{\label{fig:generel_view} Left --- the Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13} tennantite structure with coordination polyhedra around the Cu1 (blue), and the Laves polyhedra (yellow); right --- the Laves polyhedra containing Cu2 and Cu21 atoms with their partial occupancies shown as sections of spheres.}
 \end{figure}
@@
 
-According to the structural study, these deviations take place due to the distortion of \textcolor{red}{Cu\textsubscript{6}S} octahedra \textcolor{red}{(Laves polyhedra)}\cite{Tanaka2015}.
+According to the structural study, these deviations take place due to the distortion of Cu\textsubscript{6}S octahedra (Laves polyhedra)\cite{Tanaka2015}.
 The distortion at 84 K in tetrahedrite is reported to lead to either the symmetry lowering from \hmn{I -4 3 m} to \hmn{I -4 2 m}  space group accompanied by the displacement of S atoms\cite{Hathwar2019}, or to a shift of Cu2 atoms towards S\textsubscript{3} triangle plane with S\textsubscript{2} displacement\cite{Nasonova2016_2} in the same symmetry, and space group.
@@
 120 K the copper atom distribution in tennantite changes from a more statistically delocalized Cu2 to a well-defined split into Cu2 and Cu21 positions without a first-order phase transition.
-This effect is accompanied by As1 and S2 atoms displacement, which was also observed in \textcolor{red}{Ref.}~\cite{Hathwar2019}.
+This effect is accompanied by As1 and S2 atoms displacement, which was also observed in Ref.~\cite{Hathwar2019}.
 We also investigated the low- and room-temperature electronic structures of a synthetic tennantite based on the DFT calculations, which confirmed the second-order transition from the low-temperature AFM to the room-temperature PM state\cite{yaroslavzev2019}.
 
-However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves \textcolor{red}{polyhedra} in the structure, were put aside in the previous paper\cite{yaroslavzev2019}.
+However, the relationships between the peculiarities of the tennantite crystal and its electronic structures and thermoelectric properties, including the behavior of Laves polyhedra in the structure, were put aside in the previous paper\cite{yaroslavzev2019}.
 In this paper, we focus on these problems, and  investigate the tennantite cell energy distribution, and the charge density differences for different Cu positions in the Laves polyhedra.
@@
 Enraf-Nonius CAD-4 diffractometer with AgK\textsubscript{$\alpha$} equipped with graphite monochromator was used for the data collection.
-The spherical single-crystal structural study results are presented in Supplementary Material, and they are compared with the structural data \textcolor{red}{from} the \textcolor{red}{regularly shaped crystal} sample\cite{yaroslavzev2019}.
+The spherical single-crystal structural study results are presented in Supplementary Material, and they are compared with the structural data from the regularly shaped crystal sample\cite{yaroslavzev2019}.
 
@@
 The study of the high quality single crystal allowed us to re-investigate the crystal structure of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  with a high precision.
-\textcolor{red}{The structure was refined in a way similar to previously described in Ref.~\cite{yaroslavzev2019}.
+The structure was refined in a way similar to previously described in Ref.~\cite{yaroslavzev2019}.
 The sum of occupancies for Cu2, Cu21 and its symmetry related site were constrained to 1.
 Due to rather large distance between these atoms their ADP were refined independently.
-The maximum entropy method (MEM) refinement gave the result identical to \cite{yaroslavzev2019}.}
+The maximum entropy method (MEM) refinement gave the result identical to \cite{yaroslavzev2019}.
 Our data confirms that the compound contains 12 copper atoms per formula unit, and shows no evidence of copper deficiency.
-Neither XRD, nor TEM data \textcolor{red}{have shown detectable packing defects}.
+Neither XRD, nor TEM data have shown detectable packing defects.
 
@@
 Due to the crystal growth method used, the sample shows a degree of anisotropic extinction. Extinction parameters are presented in the Table~\ref{tab:anis_ext}.
-\textcolor{red}{The disorder of Cu21} is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
+The disorder of Cu21 is observed in the analyzed HAADF image of the sample in [110] zone (Fig.~\ref{fig:micro}).
 The electron diffraction, and overlay of HAADF image with the tennantite crystal [110] zone generated by VESTA\cite{Momma2011}, are given in Supplementary Material.
@@
 
-Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) \textcolor{red}{confirmed instability of this site\cite{Hathwar2019,yaroslavzev2019}}.
+Large static values for Cu2 atom (Table~\ref{tab:enst_temp}) confirmed instability of this site\cite{Hathwar2019,yaroslavzev2019}.
 This disorder is reliably described by the anharmonic model of atomic displacements using the Gram-Charlier expansion to the 4th order.
@@
 
-Within \textcolor{red}{the approach above}, the Einstein solid model is used to describe independent harmonic oscillators.
+Within the approach above, the Einstein solid model is used to describe independent harmonic oscillators.
 Thus, the low energy spectrum should consist of peaks with the Einstein's energies, which we found by DebyeFit (Table~\ref{tab:enst_temp}).
@@
 The low energy $l_{1}$ and $l_{2}$ peaks are well described by Einstein's energies of Cu2, Cu21, Cu1, and As (66, 40, 79, and 122 cm\textsuperscript{-1} respectively).
-\textcolor{red}{Same modes were observed and analyzed in tetrahedrites\cite{May2016,Lai2015} with energies approximately 4, 9 and 18 meV (33, 72, 145 cm\textsuperscript{-1}) which is
+Same modes were observed and analyzed in tetrahedrites\cite{May2016,Lai2015} with energies approximately 4, 9 and 18 meV (33, 72, 145 cm\textsuperscript{-1}) which is
 in good agreement with our results.
-Thus, we can state that the reason for the strong anharmonic behavior is a dynamic disorder of the copper atoms and arsenic atoms.}
+Thus, we can state that the reason for the strong anharmonic behavior is a dynamic disorder of the copper atoms and arsenic atoms.
 Consequently, this leads to out-of-plane low frequency rattling modes, and a low lattice thermal conductivity.
@@
 
-\subsection{Theoretical analysis of possible polytypes and morphology of Laves \textcolor{red}{polyhedra} }\label{sec:level2}
+\subsection{Theoretical analysis of possible polytypes and morphology of Laves polyhedra}\label{sec:level2}
 
@@
 As an initial point, we considered tennantite structure described in  \hmn{I -4 2 m}\ space group (henceforth called {\it reference structure}).
-The unit cell contains Laves \textcolor{red}{polyhedra} formed by copper atoms around sulphur ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
+The unit cell contains Laves polyhedra formed by copper atoms around sulphur ones (Figure~\ref{fig:init_and_opt_laves}, number 0).
 By shifting copper atoms by ca.
-1~$\angstrom$, we produced a population of structures with varying shapes of Laves \textcolor{red}{polyhedra}, which were then subjected to the procedure of unconstrained structural optimization.
-\textcolor{red}{In the DFT calculations, where we cannot have Cu2 and Cu21 at the same time since we cannot have part of an atom occupying a position within a single polyhedron, we prefer to only use Cu2 notation, but distinguish their positions before and after optimization.}
-The Laves \textcolor{red}{polyhedra} morphologies before and after the optimization are shown in Figure~\ref{fig:init_and_opt_laves}.
+1~$\angstrom$, we produced a population of structures with varying shapes of Laves polyhedra, which were then subjected to the procedure of unconstrained structural optimization.
+In the DFT calculations, where we cannot have Cu2 and Cu21 at the same time since we cannot have part of an atom occupying a position within a single polyhedron, we prefer to only use Cu2 notation, but distinguish their positions before and after optimization.
+The Laves polyhedra morphologies before and after the optimization are shown in Figure~\ref{fig:init_and_opt_laves}.
 Total energy differences between the reference structure of initial tennantite and optimized structures are shown in Figure~\ref{fig:energy_structure_rescale}.
@@
  \includegraphics[width=0.48\textwidth]{Init_and_opt_renamed}
- \caption{\label{fig:init_and_opt_laves} The geometries of SCu\textsubscript{6} Laves \textcolor{red}{polyhedra} before and after structural optimization.
+ \caption{\label{fig:init_and_opt_laves} The geometries of SCu\textsubscript{6} Laves polyhedra before and after structural optimization.
 sulphur atoms are shown in yellow, copper atoms before optimization are shown in grey, and after optimization in blue.
@@
 \caption{\label{tab:energy}%
-The difference between the reference structure energy, and the unit cell energy of tennantite with different Laves \textcolor{red}{polyhedra}.
+The difference between the reference structure energy, and the unit cell energy of tennantite with different Laves polyhedra.
 }
@@
  \includegraphics[width=0.48\textwidth]{energy_structure_rescale_ri}
- \caption{\label{fig:energy_structure_rescale} The difference between the reference structure energy and the unit cell energy of tennantite with different Laves \textcolor{red}{polyhedra}.
+ \caption{\label{fig:energy_structure_rescale} The difference between the reference structure energy and the unit cell energy of tennantite with different Laves polyhedra.
 Horizontal red line shows the reference unit cell energy.
@@
 We can also observe certain similarities between tennantite and inorganic compounds featuring atoms with  {\it 3d\textsuperscript{9}}  configuration, and having asymmetric Fermi surface.
-\textcolor{red}{The resulting complex charge distribution, and variances in the copper atom charges and, therefore, effective oxidation states, caused by structural shifts, may, in turn, be the reason for complex exchange interactions and the reported AFM ordering\cite{yaroslavzev2019} in tennantite.}
+The resulting complex charge distribution, and variances in the copper atom charges and, therefore, effective oxidation states, caused by structural shifts, may, in turn, be the reason for complex exchange interactions and the reported AFM ordering\cite{yaroslavzev2019} in tennantite.
 Moreover, the same structure features have been described for tetrahedrite\cite{DiPaola2020}.
-\textcolor{red}{The authors} noted, that understanding these features provides a key to descriptions of the phonon-limited electrical resistivity, and the Lorenz number.
+The authors noted, that understanding these features provides a key to descriptions of the phonon-limited electrical resistivity, and the Lorenz number.
 
@@
 only several~kJ/mol (1~eV~$\sim$~96.5 kJ/mol), which is on the limit of the accuracy of the method.
-This indicates, that the tennantite experimental structure may be \textcolor{red}{an averaged} result of several variations of the copper atoms shifts.
+This indicates, that the tennantite experimental structure may be an averaged result of several variations of the copper atoms shifts.
 
@@
 In conclusion, using a combination of several experimental techniques, we have investigated the structural variations of synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, manifesting itself as a dynamic disorder of the copper atoms.
-\textcolor{red}{The tennantite structure tends to conform to the asymmetric covalent polar bonds and its charge distribution is significantly affected by the atomic shifts in Laves polyhedra.
+The tennantite structure tends to conform to the asymmetric covalent polar bonds and its charge distribution is significantly affected by the atomic shifts in Laves polyhedra.
 These effects, in turn, give rise to the out-of-plane low frequency rattling modes, well described by Einstein characteristic temperatures: 74, 104, 115, and 185~K.
-The peculiarities of the tennantite crystal and electronic structure, including lattice dynamics and shifting charge distribution, shows similarities between this compound and inorganic compounds with an asymmetric Fermi surface, thus making tennantite--tetrahedrite group attractive research objects.}
+The peculiarities of the tennantite crystal and electronic structure, including lattice dynamics and shifting charge distribution, shows similarities between this compound and inorganic compounds with an asymmetric Fermi surface, thus making tennantite--tetrahedrite group attractive research objects.
 
